\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{longtable}
\begin{document}

\section*{Phase 1 Plan - Person 1 (Person A)}

\textbf{Source of truth:} \texttt{Documentation/SRS.tex}, Section 11.4, ``Phase 1: Fix Ingestion Correctness''.
\textbf{Interpretation note:} The SRS says to remove the hard-coded sports filter. For execution, this means removing brittle hard-coding, not removing filtering itself. Phase 1 should enforce a curated target-market universe so compute is spent only on markets with signal value.
\textbf{Implementation note:} Full low-cost event and market metadata sync remains enabled for the full exchange. Only expensive collectors (WebSocket, books, prices, trades, backfill) are filtered to the approved high-resolution universe.

\textbf{Phase duration:} 1-2 weeks\\
\textbf{Phase goal:} Make live data semantically usable for wallet-aware detection.

\section*{Owned Deliverables (From SRS)}
\begin{enumerate}
\item Replace the hard-coded sports-only filter with a configurable target-market selector and explicit exclusion policy.
\item Update live subscription logic so both YES and NO assets are covered.
\item Correct trade ingestion to capture condition-level identifiers.
\item Expand schema and ingestion for:
\begin{itemize}
\item \texttt{proxy\_wallet}
\item \texttt{transaction\_hash}
\item \texttt{condition\_id}
\item \texttt{asset\_id}
\item \texttt{outcome\_side}
\item \texttt{usdc\_notional}
\end{itemize}
\item Add dedupe keys and source-priority logic across WebSocket, REST, and backfill.
\end{enumerate}

\section*{Locked Implementation Decisions}
\begin{itemize}
\item Coverage policy is \textbf{Broad Cross-Domain}: include finance, macro, elections, geopolitics, commodities, energy, and crypto-policy events that can move finance.
\item Candidate-review guardrail is enabled: excluded but high-liquidity or secondary-keyword events are surfaced for review instead of being silently ignored.
\item NO coverage is required for asset-level WebSocket, order-book, and price polling.
\item Trade ingestion uses \texttt{condition\_id} against the Polymarket Data API and uses returned \texttt{asset} and \texttt{outcome} fields instead of issuing separate YES and NO trade requests.
\item Fresh-wallet readiness means \texttt{first-seen in our archive}, not ``new to Polymarket.''
\end{itemize}

\section*{Concrete Execution Breakdown}
\begin{longtable}{p{0.28\linewidth}p{0.32\linewidth}p{0.30\linewidth}}
\textbf{Work Item} & \textbf{Artifact} & \textbf{Done Condition} \\
Target-market selector refactor & Config keys plus allowlist/blocklist filter update & No hard-coded category filter remains in ingestion path, and only approved markets are ingested \\
YES/NO subscription coverage & Subscription code and coverage check output & Both outcome-side assets appear in live stream for sampled markets \\
Identifier correctness fix & Parser and persistence updates & \texttt{condition\_id} is populated for valid incoming trades \\
Schema expansion & DB migration and write-path update & Wallet-aware trade fields plus \texttt{dedupe\_key} and \texttt{source\_priority} are populated when source payload provides them \\
Dedupe and source priority & Deterministic merge rule implementation & Duplicate inflation bounded and reproducible across WS/REST/backfill \\
\end{longtable}

\section*{Execution Sequence (No Day Timeline)}
\textbf{Block 1: Target universe controls}
\begin{itemize}
\item Remove hard-coded sports-only logic and replace it with a configurable target-market selector.
\item Define strict allowlist and blocklist rules so low-value or nonsensical markets are excluded by policy while broad cross-domain finance movers stay in scope.
\item Add config validation and safe defaults so the collector fails closed rather than ingesting the full exchange.
\item Keep candidate-review output for excluded but potentially finance-relevant events.
\item Share the target-universe contract with Person 2 for validation scripts.
\end{itemize}

\textbf{Block 2: Market coverage correctness}
\begin{itemize}
\item Update subscription logic for both YES/NO assets inside the approved target universe only.
\item Run sampling script to prove both-side coverage on approved live markets.
\item Deliver coverage sample output to Person 2.
\end{itemize}

\textbf{Block 3: Field and schema integrity}
\begin{itemize}
\item Fix ingestion mapping so trade collection uses \texttt{condition\_id} correctly.
\item Implement schema migration for wallet-aware trade fields and dedupe metadata.
\item Backfill recent window to validate post-migration writes.
\end{itemize}

\textbf{Block 4: Dedupe and stabilization}
\begin{itemize}
\item Implement dedupe keys and source-priority merge policy.
\item Validate deterministic behavior across WebSocket, REST, backfill.
\item Publish Phase 1 engineering handoff notes and runbook deltas.
\end{itemize}

\section*{Handoffs to Person 2}
\begin{itemize}
\item Final target-market selector rules, including allowlist and exclusion logic.
\item Candidate-review output format for excluded but review-worthy events.
\item Final canonical field map for all required Phase 1 columns.
\item Source-priority and dedupe rule specification.
\item Sample datasets before and after dedupe for QA review.
\item SQL snippets for both-side asset coverage checks within the approved universe.
\end{itemize}

\section*{Gate 1 Checklist (Person 1 Ownership)}
\begin{itemize}
\item No hard-coded sports-only filter remains in the ingestion path.
\item Approved-market selector is active and blocks out-of-scope markets.
\item Candidate-review output surfaces excluded events that may still matter for finance.
\item YES/NO live coverage proven with evidence.
\item Required wallet and condition fields are persisted.
\item Dedupe behavior documented and reproducible.
\end{itemize}

\end{document}
