\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{longtable}
\begin{document}

\section*{Phase 2 Plan - Person 1 (Person A)}

\textbf{Source of truth:} \texttt{Documentation/SRS.tex}, Section 11.4, ``Phase 2: Build the Durable Data Plane''.
\textbf{Interpretation note:} Phase 2 is where ingestion stops being an ad hoc collector and becomes a replayable local data system. Raw payload retention, deterministic archive layout, local downstream transport, and canonical database migration all have to land together.
\textbf{Implementation note:} Phase 1 filtering and market-universe policy remain in force. Phase 2 does not widen scope; it hardens local capture, transport, and storage so the approved universe can be reconstructed exactly from raw archives.

\textbf{Phase duration:} 2-3 weeks\\
\textbf{Phase goal:} Make ingestion replayable and move canonical operational state off SQLite.

\section*{Owned Deliverables (From SRS)}
\begin{enumerate}
\item Implement raw event envelope persistence for every inbound payload.
\item Write raw archives to local disk with deterministic partitioning and manifest tracking.
\item Stand up a local normalized-envelope log and publish detector inputs downstream.
\item Provision local PostgreSQL and migrate canonical write paths.
\item Add archive manifest tables, schema version tables, and operational migration notes.
\end{enumerate}

\section*{Locked Implementation Decisions}
\begin{itemize}
\item Raw payload capture is mandatory for every inbound source path used by the system, including WebSocket, REST trades, backfill, price, and metadata sync where applicable.
\item Raw archives are immutable append-only records; normalization bugs are fixed downstream, not by mutating historical raw payloads.
\item Archive partitioning must be deterministic and replay-friendly, using stable source, date, and hour boundaries plus manifest tracking.
\item Local PostgreSQL becomes the canonical operational store in Phase 2; SQLite may remain as a local bootstrap or developer convenience layer but not as the source of truth.
\item Normalized envelopes published downstream must preserve source provenance, capture time, schema version, and sufficient identifiers to reconstruct market, asset, and wallet state.
\end{itemize}

\section*{Concrete Execution Breakdown}
\begin{longtable}{p{0.28\linewidth}p{0.32\linewidth}p{0.30\linewidth}}
\textbf{Work Item} & \textbf{Artifact} & \textbf{Done Condition} \\
Raw envelope persistence & Durable raw-envelope writer integrated into collectors & Every inbound payload path emits a stored raw envelope with source, captured-at, payload body, and schema version metadata \\
Archive and manifest pipeline & Local archive writer plus manifest tables & Raw files land in deterministic local partitions and every partition is traceable via manifest metadata \\
Normalized transport plane & Local normalized-envelope log, publisher, and normalized envelope contract implementation & Approved normalized envelopes publish successfully with reproducible ordering metadata and source provenance \\
Canonical database migration & Local PostgreSQL schema, connection layer, and migrated write paths & Canonical operational writes succeed against PostgreSQL for active collectors \\
Operational migration package & Schema-version tables plus runbook and migration notes & Replay, rollback, and cutover behavior are documented and executable by the team \\
\end{longtable}

\section*{Execution Sequence (No Day Timeline)}
\textbf{Block 1: Raw capture foundation}
\begin{itemize}
\item Introduce a shared raw-envelope format that wraps every inbound payload with source, capture timestamp, schema version, and ingestion metadata.
\item Hook raw persistence into each collector path without changing the payload semantics seen by the existing normalization layer.
\item Add minimal operational metrics so dropped raw-envelope writes are visible immediately.
\end{itemize}

\textbf{Block 2: Durable archive and manifest tracking}
\begin{itemize}
\item Implement deterministic archive partitioning for local-disk writes so replay windows can be addressed precisely by source and time bucket.
\item Add archive manifest tables and manifest-writing logic for partition completeness, file counts, byte counts, and watermark tracking.
\item Define archive naming and retention conventions that Person 2 can consume in replay tooling without special-case logic.
\end{itemize}

\textbf{Block 3: Downstream transport and canonical database cutover}
\begin{itemize}
\item Stand up a local normalized-envelope log for detector inputs emitted from the approved universe pipeline.
\item Provision local PostgreSQL schema equivalents for canonical state currently persisted in SQLite.
\item Migrate write paths incrementally so canonical tables write to PostgreSQL while preserving source compatibility for the rest of the collector stack.
\item Validate that PostgreSQL-backed writes preserve field semantics introduced in Phase 1, especially condition, asset, wallet, and dedupe metadata.
\end{itemize}

\textbf{Block 4: Operational hardening and handoff}
\begin{itemize}
\item Add schema-version tables and migration bookkeeping so replay tooling can reason about versioned payloads.
\item Publish operational migration notes covering cutover sequence, rollback path, and replay prerequisites.
\item Deliver archive layout, manifest conventions, and normalized-envelope examples to Person 2 for replay validation and the one-hour reconstruction proof.
\end{itemize}

\section*{Handoffs to Person 2}
\begin{itemize}
\item Canonical raw-envelope schema and examples from each inbound source.
\item Archive partitioning convention, manifest schema, and naming rules.
\item Normalized-envelope contract and field provenance notes.
\item Local PostgreSQL schema map and differences from prior SQLite semantics.
\item Replay prerequisites, schema-version notes, and known operational constraints.
\item One reproducible archive window for the Gate 2 replay proof.
\end{itemize}

\section*{Gate 2 Checklist (Person 1 Ownership)}
\begin{itemize}
\item Every active inbound collector path emits raw envelopes.
\item Raw archives land in immutable deterministic partitions with manifest coverage.
\item Local normalized-envelope logging publishes detector inputs with provenance and version metadata.
\item PostgreSQL accepts canonical operational writes and is treated as authoritative.
\item Archive manifest tables and schema-version tables are populated.
\item Migration and cutover notes are complete enough for shared execution.
\end{itemize}

\end{document}
