\documentclass{article}
\usepackage[margin=1in]{geometry}
\begin{document}

\section*{Phase 11 Runtime Mode Decision}

\textbf{Purpose:} remove ambiguity about what Phase 4 and Phase 6 mean in the
live local runtime after the Phase 11 startup and detector repairs.\\
\textbf{Source of truth:} \texttt{Documentation/SRS.tex},
\texttt{Documentation/phases/phase8\_v1\_operating\_mode.tex},
\texttt{Documentation/phases/phase11\_runtime\_revision.tex}, and the current
repo runtime entrypoints.

\section*{Decision}

\textbf{Decision 1: Phase 4 is part of the canonical live runtime.}

The local canonical default runtime profile is now
\texttt{alert\_live}. In that profile:
\begin{itemize}
\item Phase 3 detection is enabled and required.
\item Phase 4 evidence, alert creation, suppression, and delivery-attempt
logging are enabled as the authoritative downstream path.
\item Delivery channels may still be locally disabled, but the runtime remains
truthfully \texttt{alert\_live} if it is persisting evidence, alerts, and
delivery-attempt rows.
\end{itemize}

\textbf{Decision 2: Phase 6 is shadow-only and optional in live runtime.}

Phase 6 remains part of the canonical v1 operating story as
\texttt{rule\_based\_plus\_shadow\_ml}, but it is \textbf{not} the default live
profile on a fresh machine. Instead:
\begin{itemize}
\item Phase 6 shadow-live scoring is an explicit extension named
\texttt{shadow\_live}.
\item It should only be enabled after a shadow model is registered and
activated in \texttt{model\_registry}.
\item Phase 6 remains non-authoritative: it may score, log, and inform later
evaluation, but it does not own alert decisions.
\end{itemize}

\section*{Runtime Profiles}

\begin{itemize}
\item \texttt{collector\_only}: explicit maintenance mode only.
\item \texttt{detector\_live}: Phase 3 live, Phase 4 disabled.
\item \texttt{alert\_live}: Phase 3 live plus Phase 4 live. This is the
canonical default local runtime profile.
\item \texttt{shadow\_live}: Phase 3 live plus Phase 4 live plus Phase 6
shadow-live scoring. This is an explicit extension, not the default.
\end{itemize}

\section*{Operator Consequence}

The repo must now say two different things clearly:
\begin{itemize}
\item what the runtime is \textbf{configured} to do, and
\item what the database shows it has \textbf{recently persisted}.
\end{itemize}

The canonical command path therefore includes runtime status inspection so the
workspace can distinguish:
\begin{itemize}
\item historical offline artifacts,
\item detector-live operation,
\item alert-live operation,
\item and shadow-live operation.
\end{itemize}

\section*{Bottom Line}

The honest Phase 11 decision is:
\begin{itemize}
\item Phase 4 is canonical live by default.
\item Phase 6 is a shadow-live extension, enabled only after explicit model
activation.
\item The canonical v1 operating mode remains
\texttt{rule\_based\_plus\_shadow\_ml}, but the default local runtime profile is
\texttt{alert\_live}, not \texttt{shadow\_live}.
\end{itemize}

\end{document}
