\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{longtable}
\usepackage{enumitem}
\begin{document}

\section*{Phase 12 Repo Organization and Cleanup Plan}

\textbf{Date:} May 15, 2026\\
\textbf{Purpose:} Separate source, evidence, generated local state, and prune candidates so the repo can move into the next phase without carrying avoidable clutter or deleting useful proof artifacts.

\section*{Current Shape}
\begin{longtable}{p{0.24\linewidth}p{0.18\linewidth}p{0.46\linewidth}}
\textbf{Path} & \textbf{Observed size} & \textbf{Decision} \\
\texttt{database/} & \texttt{27G} & Keep for now. Almost all size is \texttt{polymarket\_state.db}; this is local runtime state and should be moved, compacted, or backed up before deletion. \\
\texttt{data/} & \texttt{239M} & Keep for now. Raw and detector-input archives were already pruned; \texttt{data/replay\_runs} is still replay evidence. \\
\texttt{logs/} & \texttt{45M} & Safe to prune after stopping active collectors, but keep a short final tail if debugging runtime startup. \\
\texttt{venv/} & \texttt{268M} & Keep ignored. It can be deleted and rebuilt, but doing so is not required for repo organization. \\
\texttt{reports/} & \texttt{2.0M} & Keep. These are phase evidence artifacts. \\
\texttt{Documentation/} & \texttt{2.9M} & Keep source \texttt{.tex} and important \texttt{.pdf}; generated aux/log artifacts are ignored. \\
\texttt{Old-content/} & \texttt{84K} & Archive or delete after confirming no current scripts import it. It is small, so it is not a storage blocker. \\
\texttt{\_\_pycache\_\_}, \texttt{.DS\_Store} & small & Safe to delete immediately; these are generated local noise. \\
\end{longtable}

\section*{What We Deleted Now}
Generated repo-level \texttt{.DS\_Store} files and Python cache directories outside \texttt{venv/} were removed. These are ignored by git and can be regenerated by the OS/Python.

\section*{Do Not Delete Yet}
\begin{itemize}[nosep]
\item \texttt{database/polymarket\_state.db}: huge, but it contains the current local operational state, wallet materialization, and CLOB V2 fee snapshots.
\item \texttt{reports/phase5}, \texttt{reports/phase10}, \texttt{reports/phase11}, \texttt{reports/phase12}: these are evidence for project claims.
\item \texttt{data/replay\_runs}: replay evidence until SSD-backed replay is fully wired and verified.
\item \texttt{logs/collector.log}: can be pruned, but only after deciding whether the latest runtime errors are needed for debugging.
\end{itemize}

\section*{Recommended Organization}
\begin{enumerate}[nosep]
\item Keep root runner scripts for now, but add a later consolidation pass into \texttt{scripts/phase*/} only after Phase 12 is stable.
\item Keep \texttt{database/} for schema and runbooks; move large DB files out of repo root only through env config such as \texttt{POLYMARKET\_SQLITE\_PATH}.
\item Keep phase modules \texttt{phase3/} through \texttt{phase10/}; they are still referenced by runners and reports.
\item Treat \texttt{Old-content/} as an archive candidate. If no one needs the notebooks or old monitor, remove it in a dedicated cleanup commit.
\item Add cleanup reports under \texttt{reports/phase12/} instead of deleting phase evidence.
\end{enumerate}

\section*{CLOB V2 Compatibility Boundary}
The repo now has CLOB V2 public-data smoke and fee-rate refresh tooling. That is enough for collection, wallet refresh, evidence, and paper-trading disclosure. Full CLOB V2 trading compatibility would require a separate implementation of V2 SDK or raw order signing, pUSD collateral handling, builder code attribution, and order lifecycle tests. That is intentionally outside the current runtime.

\section*{Next Cleanup Actions}
\begin{enumerate}[nosep]
\item Stop active collectors if running.
\item Rotate or truncate \texttt{logs/} after saving any useful tail.
\item Move \texttt{database/polymarket\_state.db} to SSD or another configured location if local disk pressure returns.
\item Run SQLite \texttt{VACUUM} only after deleting old rows or after moving to a backup-safe location.
\item Decide whether \texttt{Old-content/} should be deleted or kept as historical archive.
\end{enumerate}

\end{document}
