\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{longtable}
\usepackage{enumitem}
\begin{document}

\section*{Phase 12 Wallet Runtime Hardening Plan}

\textbf{Date:} May 16, 2026\\
\textbf{Purpose:} Convert the remaining whole-project gaps into an implementation plan for a mature wallet-aware runtime: first-class wallet/profile/cluster state, organic live proof, production delivery proof, evidence benchmarking, larger shadow-ML evidence, and SSD-backed replay.

\section*{Executive Target}
The target is \textbf{not} to turn the project into an autonomous trading system. The target is to make the existing local-first research/runtime system mature enough that it can honestly claim:
\begin{itemize}[nosep]
\item wallet entities are first-class tables, not only nullable fields on trades,
\item live runtime evidence comes from an organic post-prune run, not only a bounded synthetic proof,
\item alert delivery is proven through at least one real outbound provider or a clearly documented provider-disabled fallback,
\item evidence retrieval quality is benchmarked instead of assumed,
\item shadow ML evidence is expanded beyond the current small held-out packet,
\item archived replay can run from the attached SSD without copying the full archive back to internal disk,
\item CLOB V2 compatibility is explicitly checked before new organic runtime proof.
\end{itemize}

\section*{Current Baseline}
\begin{longtable}{p{0.28\linewidth}p{0.58\linewidth}}
\textbf{Area} & \textbf{Current truth} \\
Trade wallet fields & \texttt{trades} has \texttt{proxy\_wallet}, \texttt{transaction\_hash}, \texttt{condition\_id}, \texttt{outcome\_side}, and \texttt{usdc\_notional}; \texttt{canonical\_trades} exposes these fields. \\
Wallet entity plane & First-class SRS tables are now present in SQLite and Postgres schema. The first materialization produced 212 wallets, 212 activity rows, 212 first-seen rows, and 10 heuristic clusters. Profile/position enrichment is still provider-disabled/not implemented. \\
Live proof & Phase 11 has bounded Phase 3/4 proof plus one Phase 6 shadow score. Phase 12 has multiple organic runtime smokes, including a 60-minute post-lock-hardening run; the remaining proof gap is a Telegram-enabled 3--6 hour organic window. \\
Delivery proof & Phase 4 delivery classes exist for no-op, Telegram, and Discord. Telegram real delivery is now proven with HTTP 200 in \texttt{reports/phase12/delivery\_smoke.json}; Discord remains disabled. \\
Evidence proof & Phase 10 has real-provider evidence artifacts; the latest bounded Phase 11 proof used local/no-op evidence. Retrieval quality is not benchmarked as a dataset. \\
ML proof & Phase 10 LightGBM beats required baselines on a 96-row held-out packet and is registered as active shadow model \texttt{phase10\_task4\_lightgbm\_v1}. A Phase 12 live shadow pass scored 36 recent candidates into \texttt{reports/phase6/live\_shadow/...03-25-47+00-00.json}. Current live alerts do \textbf{not} use LightGBM: \texttt{POLYMARKET\_ENABLE\_PHASE6\_SHADOW\_MODE=false} and \texttt{POLYMARKET\_ENABLE\_PHASE6\_LIVE\_RUNTIME=false}. \\
Replay storage & \texttt{data/raw} and \texttt{data/detector\_input} were copied to the attached SSD and pruned locally; local replay now needs SSD-aware archive paths or restore steps. \\
CLOB V2 & Polymarket CLOB V2 is live. Current repo collection uses public CLOB/Data API/WebSocket endpoints rather than order signing, so the immediate risk is stale assumptions around fee metadata and smoke coverage rather than a trading SDK migration. \\
\end{longtable}

\section*{Unfinished Work Register: May 16, 2026}
This is the current authoritative list of what is \textbf{not fully done yet}. Earlier sections remain useful for background, but this register should drive final implementation.

\begin{longtable}{p{0.22\linewidth}p{0.31\linewidth}p{0.33\linewidth}}
\textbf{Area} & \textbf{Current truth} & \textbf{Done means} \\
Market traceability in alerts & Implemented. \texttt{reports/phase12/alert\_market\_link\_smoke.json} proves a stored alert payload and Telegram/Discord preview include \texttt{market\_slug}, \texttt{event\_slug}, \texttt{condition\_id}, \texttt{market\_url}, and \texttt{event\_url}. The clickable \texttt{market\_url} now uses the stable event URL; the outcome slug remains separate. & Keep this covered in future alert changes and avoid using brittle market-slug frontend URLs as the primary click-through. \\
Telegram production path & \texttt{reports/phase12/delivery\_smoke.json} now proves real Telegram delivery with \texttt{telegram\_configured=true}, \texttt{telegram\_sent=true}, and HTTP 200. \texttt{.env.runtime} enables Telegram and ignored \texttt{.env.runtime.secrets} supplies credentials. & Rotate the exposed bot token, keep secrets out of git, and run the next organic proof with Telegram delivery enabled. \\
Wallet profiles and positions & Wallet entity/activity/cluster tables exist and are partially populated, but \texttt{wallet\_profiles} and \texttt{wallet\_positions} are still empty in the current DB. & Either profile/position refreshers populate provider-backed rows for top wallets, or the final scope memo states these are disabled because public provider/rate budget is unavailable. \\
Archive reconciliation & \texttt{run\_phase12\_archive\_reconciliation.py} now produces an explicit operator report. Current status is \texttt{external\_archive\_not\_visible}: this shell sees only \texttt{/Volumes/Macintosh HD}, no accepted SSD archive root, and 3{,}075 partitions remain missing. & With SSD visible, auto-discovery or \texttt{--external-root /absolute/path/to/archive} resolves archived partitions and the report separates \texttt{archive\_only} from genuinely missing files. \\
Evidence benchmark & Evidence workers and real-provider artifacts exist, but retrieval quality is not measured against a labeled case set. & A benchmark runner and 20--50 labeled cases produce precision-like agreement, latency, timeout, and error-rate metrics. \\
Shadow ML scale & LightGBM exists, is registered as active shadow model, beat baselines on a small held-out packet, and has now scored 36 recent live candidates in shadow-only mode. It was \textbf{not} used for the Telegram alert; current alerts are Phase 3/4 rule-based. & Decide whether to include Phase 6 live shadow scoring in the next longer proof. It must remain shadow-only, with no alert promotion, until a later model-promotion memo. \\
Long organic proof & A 60-minute organic run passed after lock hardening, and a 3-minute post-reconciliation smoke passed. & After alert-link and archive reconciliation fixes, run a 3--6 hour organic proof with fresh raw/detector/candidate/evidence/alert deltas and clean shutdown. \\
Provider/API backpressure & Runtime survives provider timeouts and WebSocket reconnects, and the latest connectivity gate passed for Gamma events, Gamma markets, CLOB time/book, and Data API trades. A 5-minute provider-healthy smoke produced fresh raw/detector/trade/candidate/evidence/alert deltas. & Keep configurable backoff/concurrency and re-run the connectivity gate before longer 24/7-style proofs. \\
Live alert freshness & Telegram delivery works, but earlier smokes showed startup could flush old candidates and make them look like current alerts. & Live mode now uses \texttt{POLYMARKET\_PHASE4\_RUNTIME\_MAX\_CANDIDATE\_AGE\_MINUTES}; keep it at 120 minutes for 24/7 use and set it to 0 only for deliberate backlog/replay drains. \\
Alert normalization & A 5-minute provider-healthy smoke created 10 alerts and 18 delivery attempts, proving the pipeline but exposing a Telegram noise risk. An attempted 30-minute run was stopped early after 7 Telegram sends showed that the original per-pass cap was still too noisy. & Event-level cooldown, minimum delivery severity, per-pass delivery budget, and hourly delivery budget are implemented and covered by \texttt{reports/phase12/alert\_normalization\_smoke.json}. Defaults are now \texttt{max\_deliveries\_per\_pass=1} and \texttt{max\_deliveries\_per\_hour=6}; \texttt{organic\_runtime\_smoke\_alert\_hourly\_budget\_3min.json} proves zero delivery attempts while the hourly budget was full. \\
\end{longtable}

\section*{Final Finish Plan}
\subsection*{P1 Alert Payload and Click-Through Market Links}
\textbf{Status:} Implemented. Proof: \texttt{reports/phase12/alert\_market\_link\_smoke.json}.\\
\textbf{Files:} \texttt{phase4/repository.py}, \texttt{phase4/alerts.py}, delivery smoke/report docs.

\begin{enumerate}[nosep]
\item Extend \texttt{Phase4Repository.pending\_candidates()} to join \texttt{markets.slug}, \texttt{markets.condition\_id}, and \texttt{events.slug}.
\item Add a small URL builder that emits:
\begin{itemize}[nosep]
\item \texttt{event\_url = https://polymarket.com/event/<event\_slug>}
\item \texttt{market\_url = event\_url} as the stable clickable frontend URL,
\item \texttt{market\_slug\_url = https://polymarket.com/event/<market\_slug>} for diagnostics only when the market slug exists.
\end{itemize}
\item Add these fields into \texttt{render\_alert\_payload()}: \texttt{market\_slug}, \texttt{event\_slug}, \texttt{condition\_id}, \texttt{market\_url}, \texttt{event\_url}.
\item Update Telegram and Discord text renderers to include \texttt{Market: <market\_url>} and \texttt{Condition: <condition\_id>}.
\item Add or update a smoke report showing one stored alert payload with the clickable market URL.
\end{enumerate}

\textbf{Acceptance:} given an alert id, an operator can read the DB payload or Telegram message, tap the event-backed market URL, and land on the Polymarket event while using the outcome slug and condition id to identify the exact outcome.

\subsection*{P2 Real Telegram Delivery Proof}
\textbf{Status:} Real Telegram proof complete. Proof: \texttt{reports/phase12/delivery\_smoke.json}.\\
\textbf{Files:} \texttt{run\_phase4\_delivery\_smoke.py} or equivalent, \texttt{.env.runtime.example}, \texttt{reports/phase12/delivery\_smoke.json}.

\begin{enumerate}[nosep]
\item Keep secrets out of git; use shell env or \texttt{.env.runtime.secrets}.
\item Send one redacted test payload with a market URL through Telegram.
\item Persist/report provider status, HTTP result, provider message id if available, and redacted request payload.
\item If secrets are absent, produce an honest \texttt{provider\_disabled} report instead of claiming delivery.
\item After the current exposed-token test, rotate the Telegram bot token before long-running use.
\end{enumerate}

\textbf{Acceptance:} satisfied for Telegram: \texttt{telegram\_sent=true}. Keep Discord marked disabled unless configured later.

\subsection*{P3 Wallet Profile and Position Completion}
\textbf{Files:} \texttt{run\_wallet\_entity\_materializer.py}, new \texttt{run\_wallet\_profile\_refresh.py}, new \texttt{run\_wallet\_position\_refresh.py} if provider endpoints are reliable.

\begin{enumerate}[nosep]
\item Re-run wallet entity and cluster materializers after the newest live data.
\item Select top wallets by recent notional, candidate involvement, and cluster centrality.
\item Try public profile/position endpoints only behind explicit enable flags and rate limits.
\item Store provider responses in \texttt{wallet\_profiles} and \texttt{wallet\_positions}, or write a report explaining provider-disabled status.
\end{enumerate}

\textbf{Acceptance:} \texttt{wallet\_profiles} and \texttt{wallet\_positions} are either non-zero with a report, or explicitly documented as out of scope for this release.

\subsection*{P4 Archive Reconciliation With SSD Visible}
\textbf{Files:} \texttt{run\_phase12\_archive\_reconciliation.py}, \texttt{phase7/storage.py}, \texttt{phase7/runtime\_storage.py}, \texttt{.env.runtime}, \texttt{reports/phase12/archive\_reconciliation.json}.

\begin{enumerate}[nosep]
\item Confirm the SSD is visible under \texttt{/Volumes/...} in the same shell that runs Codex.
\item Run \texttt{run\_phase12\_archive\_reconciliation.py --env-file .env.runtime --json}.
\item If auto-discovery does not find the archive root, rerun with \texttt{--external-root /absolute/path/to/archive}.
\item Verify the report distinguishes local, external-archive, and genuinely missing partitions.
\end{enumerate}

\textbf{Acceptance:} \texttt{missing\_file\_count} drops for partitions present on SSD, and \texttt{archive\_only\_count} rises instead of hiding the fact that files are external. If the SSD is not visible, the report must remain \texttt{external\_archive\_not\_visible} rather than implying replay readiness.

\subsection*{P5 Evidence Benchmark}
\textbf{Files:} \texttt{config/evidence\_benchmark\_cases.json}, \texttt{run\_evidence\_benchmark.py}, \texttt{reports/phase12/evidence\_benchmark.json}.

\begin{enumerate}[nosep]
\item Create 20--50 representative cases across politics, sports, crypto, companies, and time-sensitive markets.
\item Label expected evidence state: \texttt{already\_public}, \texttt{weak\_public}, \texttt{silent}, or \texttt{unknown}.
\item Reuse the Phase 4 evidence provider stack.
\item Report agreement, timeout rate, provider latency, and classification drift.
\end{enumerate}

\textbf{Acceptance:} final docs can say evidence retrieval was benchmarked with known limitations, not merely assumed.

\subsection*{P6 Shadow ML Dataset Expansion}
\textbf{Files:} replay/backtest CLIs, \texttt{reports/phase12/shadow\_ml\_dataset\_expansion.json}, \texttt{reports/phase12/shadow\_ml\_baseline\_comparison.json}.

\begin{enumerate}[nosep]
\item Use SSD-backed replay windows to generate a larger validation dataset.
\item Preserve train/validation/test time splits.
\item Add wallet aggregate features once P3 is complete or explicitly mark them unavailable.
\item Compare wallet-aware and wallet-unaware baselines.
\end{enumerate}

\textbf{Acceptance:} row count materially exceeds the 96-row packet, and the final claim remains shadow-only.

\subsection*{P7 Provider Backpressure and Long Organic Proof}
\textbf{Files:} collector HTTP/config modules, live-smoke report.

\begin{enumerate}[nosep]
\item Add/env-expose conservative CLOB/Data API concurrency, batch-size, timeout, and retry settings.
\item Emit timeout/retry counters into live-smoke reports.
\item Run a 3--6 hour organic proof after P1--P4.
\end{enumerate}

\textbf{Acceptance:} the long report shows clean shutdown, fresh data deltas, timeout/retry metrics, and no unhandled collector crash.

\section*{Progress Update: May 15, 2026}
\begin{longtable}{p{0.28\linewidth}p{0.58\linewidth}}
\textbf{Area} & \textbf{Latest result} \\
Wallet plane & Implemented schema and materializers: \texttt{run\_wallet\_trade\_refresh.py}, \texttt{run\_wallet\_entity\_materializer.py}, and \texttt{run\_wallet\_cluster\_materializer.py}. Latest reports live under \texttt{reports/phase12/}. \\
CLOB V2 public-data compatibility & \texttt{run\_clob\_v2\_smoke.py} passed for server time, book, Data API trades, and WebSocket subscription shape. \texttt{run\_clob\_v2\_fee\_refresh.py} captured active token fee-rate payloads. \\
SSD-backed replay & Mounted T7 archive replay is proven. \texttt{runtime\_replay\_t7\_30min\_bounded.json} processed 2{,}000 envelopes, 3{,}792 snapshots, and 3 trades with zero missing restore items. \\
Organic live smoke & \texttt{organic\_runtime\_smoke\_1min\_clean.json} passed controlled shutdown: runtime exit code 0, raw archive +300{,}646{,}711 bytes, detector input +2{,}335{,}735 bytes, and 10 new evidence snapshots. \\
Shutdown tooling & \texttt{run\_phase12\_live\_smoke.py} now launches the runtime in its own process group and terminates that group after the bounded run, preventing orphan child logs/processes. \\
\end{longtable}

\section*{Implementation Principles}
\begin{enumerate}[nosep]
\item Keep rule-based Phase 4 alerts authoritative; ML remains shadow-only until a later promotion memo.
\item Build wallet identity as public-wallet intelligence only. Never imply real-world identity.
\item Prefer idempotent materializers over one-off notebooks or manual SQL.
\item Every new claim needs a machine-readable report under \texttt{reports/phase12/}.
\item Keep raw archives and detector-input archives off git; rely on SSD mount or explicit restore for heavy replay.
\item Do not restart long-running collection until schema changes, storage checks, and delivery settings are known-good.
\end{enumerate}

\section*{Workstream A: First-Class Wallet/Profile/Cluster Plane}
\textbf{Goal:} Promote wallet information from trade columns into durable entity tables with materialized activity/profile/cluster state.

\subsection*{A1 Schema Additions}
Add idempotent schema blocks to \texttt{database/schema.sql} and \texttt{database/postgres\_schema.sql}:
\begin{itemize}[nosep]
\item \texttt{wallets}: one row per public wallet/proxy wallet.
\item \texttt{wallet\_first\_seen}: first observed trade/event provenance.
\item \texttt{wallet\_activity}: rolling and lifetime activity aggregates.
\item \texttt{wallet\_profiles}: optional public profile/API snapshot state.
\item \texttt{wallet\_positions}: optional current or sampled market positions.
\item \texttt{wallet\_cluster\_membership}: reversible statistical cluster labels.
\item \texttt{wallet\_entity\_runs}: materialization run ledger.
\end{itemize}

\textbf{Minimum columns:}
\begin{itemize}[nosep]
\item \texttt{wallet\_id}, \texttt{proxy\_wallet}, \texttt{first\_seen\_at}, \texttt{last\_seen\_at}, \texttt{source\_count}, \texttt{created\_at}, \texttt{updated\_at}.
\item Aggregate fields: \texttt{trade\_count}, \texttt{market\_count}, \texttt{condition\_count}, \texttt{notional\_total}, \texttt{notional\_24h}, \texttt{notional\_7d}, \texttt{avg\_trade\_size}, \texttt{last\_trade\_at}.
\item Profile fields: \texttt{profile\_source}, \texttt{profile\_status}, \texttt{profile\_json}, \texttt{profile\_captured\_at}.
\item Cluster fields: \texttt{cluster\_id}, \texttt{cluster\_version}, \texttt{method}, \texttt{confidence}, \texttt{features\_json}, \texttt{assigned\_at}.
\end{itemize}

\subsection*{A2 Materialization CLI}
Create \texttt{run\_wallet\_entity\_materializer.py}. It should:
\begin{enumerate}[nosep]
\item read \texttt{canonical\_trades} where \texttt{proxy\_wallet} is not null,
\item upsert \texttt{wallets} and \texttt{wallet\_first\_seen},
\item compute aggregate rows into \texttt{wallet\_activity},
\item write a \texttt{wallet\_entity\_runs} row,
\item emit \texttt{reports/phase12/wallet\_entity\_materialization.json}.
\end{enumerate}

\textbf{Acceptance criteria:}
\begin{itemize}[nosep]
\item command exits 0 on SQLite,
\item command can run twice without duplicating rows,
\item report includes \texttt{wallet\_count}, \texttt{wallets\_with\_first\_seen}, \texttt{activity\_rows}, null-rate metrics, and top-wallet aggregate sanity checks,
\item \texttt{run\_runtime\_status.py} or a new Phase 12 status command reports wallet-plane health.
\end{itemize}

\subsection*{A3 Profile and Position Enrichment}
Create a second CLI, \texttt{run\_wallet\_profile\_refresh.py}, after A2 is stable. It should be budgeted and optional:
\begin{itemize}[nosep]
\item select top-N wallets by recent notional or alert involvement,
\item call configured public profile/position endpoints only when enabled,
\item cache every response with timestamp, provider, status, and raw metadata,
\item fail soft when provider credentials or rate budgets are unavailable.
\end{itemize}

\textbf{Acceptance criteria:} at least one cached profile/position refresh packet exists, or the report explicitly says provider disabled with no false success.

\subsection*{A4 Cluster Baseline}
Start with transparent heuristic clusters, not graph ML:
\begin{itemize}[nosep]
\item cluster by repeated co-occurrence in the same markets/conditions,
\item use common active-window overlap and notional concentration,
\item write \texttt{wallet\_cluster\_membership} with \texttt{method=heuristic\_v1},
\item include enough features in \texttt{features\_json} to audit why the assignment happened.
\end{itemize}

\textbf{Acceptance criteria:} cluster assignments exist for wallets with sufficient overlap, and docs clearly call them statistical groups, not people.

\section*{Workstream B: Organic Live Runtime Proof}
\textbf{Goal:} Produce a post-prune organic live run that proves the normal collector/runtime path can write fresh raw archives, detector input, candidates, alerts, and status artifacts.

\subsection*{B1 Preflight}
\begin{enumerate}[nosep]
\item Confirm SSD backup remains mounted or documented.
\item Run \texttt{run\_runtime\_storage\_status.py --json}.
\item Run \texttt{run\_runtime.py --check-only}.
\item Confirm local \texttt{data/raw} and \texttt{data/detector\_input} directories exist.
\item Decide whether Phase 6 shadow live is enabled for the run.
\end{enumerate}

\subsection*{B2 Run Protocol}
\begin{itemize}[nosep]
\item Start with a \textbf{30--60 minute smoke run}.
\item If stable, run a \textbf{3--6 hour organic window}.
\item Keep a run ledger in \texttt{reports/phase12/organic\_runtime\_run.json}.
\item Capture start/end disk, row deltas, alert deltas, delivery deltas, evidence deltas, and shadow-score deltas.
\end{itemize}

\textbf{Acceptance criteria:}
\begin{itemize}[nosep]
\item new raw archive bytes > 0,
\item new detector-input bytes > 0,
\item no storage blocker,
\item no unhandled collector crash,
\item Phase 3 status is reachable,
\item if no candidate appears organically, the report says \texttt{no\_organic\_candidate\_observed} rather than forcing a synthetic proof.
\end{itemize}

\section*{Workstream C: Production-Real Alert Delivery}
\textbf{Goal:} Prove at least one real outbound alert provider path or document provider-disabled status honestly.

\subsection*{C1 Configuration}
Use repo-ignored secret handling:
\begin{itemize}[nosep]
\item \texttt{POLYMARKET\_ENABLE\_PHASE4\_TELEGRAM=true},
\item \texttt{POLYMARKET\_PHASE4\_TELEGRAM\_BOT\_TOKEN} from shell/keychain/\texttt{.env.runtime.secrets},
\item \texttt{POLYMARKET\_PHASE4\_TELEGRAM\_CHAT\_ID} from shell/keychain/\texttt{.env.runtime.secrets}.
\end{itemize}

\subsection*{C2 Delivery Smoke Test}
Create \texttt{run\_phase4\_delivery\_smoke.py}:
\begin{itemize}[nosep]
\item builds a redacted test alert payload,
\item sends to enabled delivery providers,
\item writes DB delivery attempt rows or a report-only smoke result,
\item never prints secrets,
\item emits \texttt{reports/phase12/delivery\_smoke.json}.
\end{itemize}

\textbf{Acceptance criteria:} either one provider returns a real provider message id / HTTP success, or the report explicitly says provider not configured and no production-delivery claim is made.

\section*{Workstream D: Evidence Retrieval Benchmark}
\textbf{Goal:} Measure evidence retrieval quality so ``public silence'' is no longer an assumption.

\subsection*{D1 Benchmark Dataset}
Create \texttt{config/evidence\_benchmark_cases.json} with 20--50 cases:
\begin{itemize}[nosep]
\item market/event id,
\item query text,
\item evaluation timestamp,
\item expected state: \texttt{already\_public}, \texttt{weak\_public}, \texttt{silent}, \texttt{unknown},
\item notes and source URLs where available.
\end{itemize}

\subsection*{D2 Benchmark Runner}
Create \texttt{run\_evidence\_benchmark.py}:
\begin{itemize}[nosep]
\item reuses Phase 4 provider abstraction,
\item logs provider latency, result count, state classification, and timeout rate,
\item supports \texttt{--mode live}, \texttt{--mode cache}, and \texttt{--mode mixed},
\item writes \texttt{reports/phase12/evidence\_benchmark.json}.
\end{itemize}

\textbf{Acceptance criteria:}
\begin{itemize}[nosep]
\item benchmark has at least 20 cases,
\item report includes precision-like agreement with expected state,
\item report includes timeout/error rate,
\item docs state retrieval confidence limits.
\end{itemize}

\section*{Workstream E: Shadow ML Scale-Up}
\textbf{Goal:} Expand beyond the current 96-row held-out packet while keeping ML shadow-only.

\subsection*{E1 Dataset Expansion}
\begin{itemize}[nosep]
\item Use the SSD archive path for additional replay windows.
\item Generate more Phase 5 validation rows across multiple days and market types.
\item Preserve train/validation/test window separation.
\item Add wallet-entity features from Workstream A once materialized.
\end{itemize}

\subsection*{E2 Required Reports}
\begin{itemize}[nosep]
\item \texttt{reports/phase12/shadow\_ml\_dataset\_expansion.json}
\item \texttt{reports/phase12/shadow\_ml\_baseline\_comparison.json}
\item \texttt{reports/phase12/shadow\_ml\_calibration\_review.json}
\end{itemize}

\textbf{Acceptance criteria:}
\begin{itemize}[nosep]
\item dataset row count materially exceeds 96,
\item wallet-aware model is compared to wallet-unaware baselines,
\item calibration and class balance are reported,
\item operating-mode memo still says ML is shadow-only unless a separate promotion decision is made.
\end{itemize}

\section*{Workstream F: SSD-Backed Replay}
\textbf{Goal:} Replay archived windows without recopying all raw archives to internal disk.

\subsection*{F1 Archive Path Settings}
Environment/config support now exists for:
\begin{itemize}[nosep]
\item \texttt{POLYMARKET\_RAW\_ARCHIVE\_ROOT},
\item \texttt{POLYMARKET\_DETECTOR\_INPUT\_ROOT},
\item optional \texttt{POLYMARKET\_ARCHIVE\_ROOT\_READONLY=true}.
\end{itemize}

\subsection*{F2 Replay Tooling}
Replay/storage tools should use configured archive roots:
\begin{itemize}[nosep]
\item \texttt{utils/event\_log.py}: writes raw and detector-input partitions under configured roots and stores absolute manifest paths for external roots.
\item \texttt{run\_runtime\_storage\_status.py}: reports configured roots, existence, size, and read-only state.
\item \texttt{phase7/storage.py}: resolves repo-relative and absolute manifest partition paths during storage audit.
\item \texttt{phase3/detector.py}: reads detector-input replay partitions through the configured detector-input root.
\end{itemize}

\textbf{Acceptance criteria:}
\begin{itemize}[nosep]
\item one replay window can read from \texttt{/Volumes/T7 Shield/...} after the actual SSD path is supplied,
\item internal \texttt{data/raw} can remain empty when \texttt{POLYMARKET\_RAW\_ARCHIVE\_ROOT} points to an external archive,
\item report records archive root and whether it was internal or SSD-backed,
\item missing SSD mount produces a clear error, not silent zero-row replay.
\end{itemize}

\textbf{Current proof:} \texttt{reports/phase12/runtime\_storage\_status\_ssd\_ready.json} confirms default roots; \texttt{reports/phase12/runtime\_storage\_status\_external\_roots\_smoke.json} confirms external/read-only root configuration; \texttt{reports/phase12/storage\_audit\_t7\_archive.json} confirms the mounted T7 archive is read by the storage audit; \texttt{reports/phase12/runtime\_replay\_t7\_smoke.json} confirms a bounded archived replay can process detector-input envelopes from the mounted SSD; \texttt{reports/phase12/runtime\_replay\_t7\_30min\_bounded.json} processed 2{,}000 envelopes, 3{,}792 snapshots, and 3 trades with zero missing restore items. The latest operator check, \texttt{reports/phase12/archive\_reconciliation.json}, is intentionally blocked because the SSD is not visible to the current shell.

\section*{Workstream G: CLOB V2 Compatibility}
\textbf{Goal:} Keep the runtime honest about Polymarket's CLOB V2 migration before relying on new live data proofs.

\subsection*{G1 Public Data Smoke}
Create and run \texttt{run\_clob\_v2\_smoke.py}. It should:
\begin{itemize}[nosep]
\item confirm \texttt{https://clob.polymarket.com/time} is reachable,
\item confirm \texttt{https://clob.polymarket.com/book?token\_id=...} returns a valid book for a local market token,
\item confirm \texttt{https://data-api.polymarket.com/trades?market=...} still returns list-shaped trade data,
\item record the unchanged market WebSocket subscription shape,
\item emit \texttt{reports/phase12/clob\_v2\_smoke.json}.
\end{itemize}

\textbf{Acceptance criteria:} public CLOB, Data API, and market WebSocket assumptions are checked before a long organic run; the report clearly states that order placement and V2 signing are outside the current repo scope.

\subsection*{G2 Fee and Trading Boundary}
CLOB V2 changes fee handling and order signing. The current repo should:
\begin{itemize}[nosep]
\item keep public-data collection on \texttt{https://clob.polymarket.com},
\item avoid any claim that it supports V2 order placement until a separate trading module exists,
\item record dynamic fee-rate payloads in \texttt{market\_fee\_rates} before production economic claims,
\item avoid using \texttt{base\_fee} in PnL math until the unit semantics are pinned to official docs,
\item refresh migration notes whenever Polymarket changes the public docs.
\end{itemize}

\section*{Recommended Execution Order}
\begin{longtable}{p{0.10\linewidth}p{0.30\linewidth}p{0.48\linewidth}}
\textbf{Step} & \textbf{Work} & \textbf{Reason} \\
1 & Alert-normalized 30--60 minute runtime proof & Provider connectivity and a 5-minute provider-healthy smoke now pass; re-run after the current hourly budget cools down with the stricter one-per-pass and six-per-hour Telegram budget. \\
2 & Phase 6 shadow-live decision & Decide whether to include LightGBM shadow scoring during the next proof, without using it to create alerts. A 36-candidate recent-window scoring pass already works. \\
3 & Wallet profile/position refresh decision & Completes or explicitly disables the remaining wallet-plane tables. \\
4 & Evidence benchmark dataset + runner & Makes public-silence claims measurable. \\
5 & SSD archive reconciliation and shadow ML expansion & Resume replay and larger ML dataset work when the SSD is attached again. \\
6 & Final scope memo & Updates SRS truth: mature research v1 vs production future work. \\
\end{longtable}

\section*{Next Implementation Slice}
Start with an alert-normalized 30--60 minute runtime proof. Provider connectivity now passes and the 5-minute provider-healthy smoke proved fresh collection through Phase 4. The first longer attempt was intentionally stopped because the initial budget was still noisy; the next run should use \texttt{POLYMARKET\_PHASE4\_ALERT\_MAX\_DELIVERIES\_PER\_PASS=1} and \texttt{POLYMARKET\_PHASE4\_ALERT\_MAX\_DELIVERIES\_PER\_HOUR=6}.

\textbf{Files to touch first:}
\begin{itemize}[nosep]
\item \texttt{phase4/alerts.py}
\item \texttt{config/settings.py}
\item \texttt{.env.runtime.example}
\item \texttt{run\_phase12\_live\_smoke.py}
\item \texttt{run\_runtime.py}
\item \texttt{reports/phase12/alert\_normalization\_smoke.json}
\item \texttt{reports/phase12/organic\_runtime\_smoke\_telegram\_30min.json}
\item \texttt{reports/phase12/delivery\_smoke.json}
\end{itemize}

\textbf{Do not start with:}
\begin{itemize}[nosep]
\item committing Telegram secrets,
\item PostgreSQL migration,
\item model promotion,
\item SSD replay until the SSD is attached again.
\end{itemize}

\section*{Final Claim Boundary}
After this plan is implemented, the project may claim a mature local-first wallet-aware research/runtime platform with bounded and organic live evidence, real or honestly disabled delivery, benchmarked evidence retrieval, SSD-backed replay, and shadow ML evaluation. It still should not claim autonomous trading authority, human identity inference, guaranteed profitable edge, or production high-availability infrastructure unless those are explicitly built later.

\end{document}
