\documentclass{article}
\usepackage[margin=1in]{geometry}
\begin{document}

\section*{Phase 2 Gate 2 Signoff}

\textbf{Phase:} 2\\
\textbf{Owner model:} Single owner workflow\\
\textbf{Source of truth:} \texttt{Documentation/SRS.tex}, Section 11.4\\
\textbf{Canonical phase delivery doc:} \texttt{Documentation/phases/phase2.tex}\\
\textbf{Execution branch:} \texttt{phase2-local-data-plane}\\
\textbf{Signoff date:} April 20, 2026

\section*{Summary}

This document is the Gate 2 evidence pack for the durable local data plane.
Phase 2 required the collector to move beyond a mutable live-only workflow and
become a replayable, manifest-backed, local-first system with a viable local
PostgreSQL operational path.

The engineering objective is met. Raw archive persistence, detector-input
logging, replay validation, replay republish, PostgreSQL migration, live
PostgreSQL runtime execution, and graceful shutdown behavior have all been
validated on the local machine.

\section*{Delivered Artifacts}

\begin{itemize}
\item \texttt{utils/event\_log.py}
\item \texttt{database/schema.sql}
\item \texttt{database/postgres\_schema.sql}
\item \texttt{database/postgres\_migrate.py}
\item \texttt{database/POSTGRES\_LOCAL\_RUNBOOK.md}
\item \texttt{config/settings.py}
\item \texttt{database/db\_manager.py}
\item \texttt{validation/phase2\_replay.py}
\item \texttt{validation/run\_phase2\_replay.py}
\item \texttt{validation/phase2\_republish.py}
\item \texttt{validation/run\_phase2\_republish.py}
\item Collector integrations in events, markets, trades, backfill, prices, and WS listeners
\end{itemize}

\section*{Validation Evidence}

\textbf{Replay parity proof}
\begin{itemize}
\item Replay window: \texttt{2026-04-20T05:00:00+00:00} to \texttt{2026-04-20T06:00:00+00:00}
\item Source system: \texttt{gamma\_events}
\item Raw rows in window: 66
\item Detector rows in window: 66
\item Raw partition manifest rows: 66
\item Detector partition manifest rows: 66
\item Result: exact parity for the validated one-hour window
\end{itemize}

\textbf{Replay republish proof}
\begin{itemize}
\item Replay run ID: \texttt{12bc07e8ae50}
\item Raw partitions touched: 1
\item Raw rows scanned: 66
\item Rows republished: 66
\item Output path: \texttt{data/replay\_runs/12bc07e8ae50/source\_system=gamma\_events/detector\_input.ndjson}
\item Result: deterministic replay output produced successfully
\end{itemize}

\textbf{PostgreSQL migration proof}
\begin{itemize}
\item \texttt{events}: 62,150+ rows present and later advanced by live collector execution
\item \texttt{markets}: 176,188 rows migrated
\item \texttt{trades}: 79,785 rows migrated
\item \texttt{order\_book\_snapshots}: 3,442,571 rows migrated
\item \texttt{snapshots}: 38,074,383 rows migrated
\item Final local PostgreSQL database size: approximately 12 GB
\item Result: the local PostgreSQL operational store exists at meaningful production-scale volume
\end{itemize}

\textbf{Live PostgreSQL runtime proof}
\begin{itemize}
\item The collector was executed with the PostgreSQL backend configuration on the local machine.
\item Schema application succeeded.
\item Live Gamma event paging advanced through real offsets during runtime.
\item Raw archive manifests and detector-input manifests were written during live execution.
\item Graceful shutdown was re-tested after the fix and completed cleanly.
\item Result: PostgreSQL is viable as a real local runtime backend, not only as an offline migration target
\end{itemize}

\section*{Gate 2 Checklist}

\begin{itemize}
\item Every active inbound collector path emits raw envelopes. Passed
\item Raw archives are immutable, deterministic, and manifest-backed. Passed
\item Detector inputs are published with provenance and schema version metadata. Passed
\item Replay tooling reconstructs a bounded archive window deterministically. Passed
\item Replay parity matched the validated one-hour proof window. Passed
\item Replay republish produced deterministic detector-input output. Passed
\item Local PostgreSQL accepts canonical operational data and live writes. Passed
\item Graceful collector shutdown on the PostgreSQL path is clean. Passed
\item Point-in-time contract prose is fully polished for formal review. Partial documentation follow-up only
\end{itemize}

\section*{Residual Items}

\begin{itemize}
\item Add a shorter formal prose section describing point-in-time contracts for profiles, activity, and evidence snapshots.
\item Optionally run a longer soak test if the grading rubric asks for extended uptime evidence rather than functional proof.
\item Commit and sign off the branch state once documentation wording is approved.
\end{itemize}

\section*{Signoff}

\begin{itemize}
\item Phase 2 engineering readiness: \textbf{Ready for Gate 2 signoff}
\item Remaining work category: \textbf{Documentation polish and packaging only}
\item Final assessment: \textbf{Phase 2 delivered}
\end{itemize}

\end{document}
