\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{longtable}
\begin{document}

\section*{Phase 1 Plan - Single Owner}

\textbf{Source of truth:} \texttt{Documentation/SRS.tex}, Section 11.4, ``Phase 1: Fix Ingestion Correctness''.
\textbf{Interpretation note:} Phase 1 is about making live data semantically usable for wallet-aware detection. It is not a modeling phase.
\textbf{Implementation note:} Validation is scoped to the approved target-market universe. Full low-cost metadata sync may still cover the wider exchange, but expensive live collection remains focused on the approved universe.

\textbf{Phase duration:} 1-2 weeks\\
\textbf{Phase goal:} Make live trade and market data correct enough to support trustworthy wallet-aware feature engineering later.

\section*{Owned Deliverables (From SRS)}
\begin{enumerate}
\item Replace the hard-coded sports-only filter with a configurable target-market selector and explicit exclusion policy.
\item Update live subscription logic so both YES and NO assets are covered.
\item Correct trade ingestion to capture condition-level identifiers.
\item Expand schema and ingestion for:
\begin{itemize}
\item \texttt{proxy\_wallet}
\item \texttt{transaction\_hash}
\item \texttt{condition\_id}
\item \texttt{asset\_id}
\item \texttt{outcome\_side}
\item \texttt{usdc\_notional}
\end{itemize}
\item Add dedupe keys and source-priority logic across WebSocket, REST, and backfill.
\item Write the canonical entity and field validation spec for wallet-aware trades.
\item Build validation scripts for:
\begin{itemize}
\item both-side asset coverage
\item duplicate trade inflation
\item null-rate of wallet fields
\item condition-id population rate
\end{itemize}
\item Define the first version of:
\begin{itemize}
\item \texttt{first\_seen\_at}
\item fresh-wallet flag logic
\item trade-to-market episode linkage rules
\end{itemize}
\item Produce a QA sample review over at least 20 manually inspected trade episodes.
\end{enumerate}

\section*{Locked Implementation Decisions}
\begin{itemize}
\item Coverage policy is \textbf{Broad Cross-Domain}: include finance, macro, elections, geopolitics, commodities, energy, and crypto-policy events that can move finance.
\item Candidate-review guardrail is enabled: excluded but potentially finance-relevant events must be surfaced rather than silently dropped.
\item Both YES and NO assets are required for WebSocket, order-book, price, and trade correctness.
\item Trade ingestion must use \texttt{condition\_id} semantics and preserve returned \texttt{asset}, \texttt{outcome}, \texttt{proxyWallet}, and \texttt{transactionHash} when available.
\item Fresh-wallet readiness means ``first seen in our archive,'' not ``new to Polymarket'' in an absolute sense.
\end{itemize}

\section*{Concrete Execution Breakdown}
\begin{longtable}{p{0.28\linewidth}p{0.32\linewidth}p{0.30\linewidth}}
\textbf{Work Item} & \textbf{Artifact} & \textbf{Done Condition} \\
Target-market selector refactor & Configurable universe policy and exclusion rules & No brittle sports-only hard-coding remains in the ingestion path \\
YES/NO coverage correctness & Live subscription updates and coverage proof & Both outcome-side assets appear in sampled live collection for approved markets \\
Trade schema correctness & Parser and persistence updates & \texttt{condition\_id}, asset-side fields, wallet-linked fields, and notional fields are populated when source payloads provide them \\
Dedupe and source priority & Deterministic merge rules & Duplicate inflation is measured, bounded, and reproducible across WS/REST/backfill \\
Validation contract and scripts & Field-level data contract plus automated checks & All required Phase 1 checks run reproducibly against the approved universe \\
Episode semantics and QA & Deterministic semantic rules and manual review sheet & \texttt{first\_seen\_at}, fresh-wallet logic, and episode linkage are documented, executable, and manually spot-checked \\
\end{longtable}

\section*{Execution Sequence (No Day Timeline)}
\textbf{Block 1: Target universe controls}
\begin{itemize}
\item Replace sports-only hard-coding with a configurable target-market selector.
\item Define allowlist/blocklist rules and candidate-review output for excluded but review-worthy events.
\item Freeze selector defaults and version the policy for reproducible validation.
\end{itemize}

\textbf{Block 2: Market and trade correctness}
\begin{itemize}
\item Update live logic for both YES and NO assets inside the approved universe.
\item Fix ingestion mapping so trades carry \texttt{condition\_id}, asset-side identity, wallet-linked fields, and notional values correctly.
\item Add dedupe keys and source-priority merge logic across all collection paths.
\end{itemize}

\textbf{Block 3: Validation and semantics}
\begin{itemize}
\item Write the canonical validation contract and implement the validation suite.
\item Measure both-side coverage, duplicate inflation, wallet null-rates, and condition-id population.
\item Define and test \texttt{first\_seen\_at}, fresh-wallet, and trade-to-market episode linkage rules.
\end{itemize}

\textbf{Block 4: QA and signoff}
\begin{itemize}
\item Run manual QA over at least 20 trade episodes.
\item Produce one data-quality report proving both-side and wallet-linked coverage for the approved universe.
\item Assemble one Gate 1 signoff packet.
\end{itemize}

\section*{Gate 1 Checklist}
\begin{itemize}
\item Approved-universe selector behavior is versioned and validated.
\item YES/NO coverage is live for the approved universe.
\item Wallet-linked trade fields and condition-level identifiers are landing correctly.
\item Dedupe and source-priority logic are implemented and measurable.
\item Automated validation suite produces reproducible outputs.
\item \texttt{first\_seen\_at}, fresh-wallet, and episode-linkage rules are deterministic.
\item Manual review of at least 20 episodes is complete.
\item One Gate 1 signoff document is ready.
\end{itemize}

\end{document}
