\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{longtable}
\begin{document}

\section*{Phase 9 Plan - Single Owner}

\textbf{Source of truth:} \texttt{Documentation/SRS.tex}, especially Section 2.5 ``Implementation Readiness Checklist'', Section 2.6 ``Definition of v1 Complete'', Section 8 ``Replay, Backtesting, and Validation'', Section 9 ``Operations, Security, and Governance'', and Section 11 ``Roadmap and Stage Gates'', plus the Phase 8 closeout set in \texttt{Documentation/phases/phase8\_reference\_path.tex}, \texttt{Documentation/phases/phase8\_v1\_operating\_mode.tex}, \texttt{Documentation/phases/phase8\_metrics\_review.tex}, and \texttt{Documentation/phases/phase8\_final\_closeout.tex}.\\
\textbf{Execution status:} Planned single-owner follow-on after Phase 8 closeout.\\
\textbf{Entry assumption:} Phase 1 through Phase 8 already established the canonical repo structure, the local-first operating mode, and the exact reasons the project is still not defensible as fully SRS-complete v1 in the current workspace snapshot.

\textbf{Phase goal:} Convert the repo from \textbf{provenance-complete but evidence-incomplete} into a materially populated, replay-defensible, single-owner v1 package that satisfies the remaining SRS completion requirements.\\
\textbf{Interpretation note:} The original SRS roadmap ends at Phase 7, and Phase 8 already handled single-owner consolidation and truthfulness. Phase 9 is therefore not a new aspirational research phase. It is a \textbf{single-owner remediation and evidence-materialization phase} derived from the SRS completion contract and from the explicit ``not yet'' result recorded in Phase 8.\\
\textbf{Implementation note:} There is no Person 1 / Person 2 split for Phase 9. Historical split runbooks and notes remain useful inputs, but Phase 9 ownership is intentionally unified into one end-to-end workflow.

\section*{Why Phase 9 Exists}
Phase 8 clarified that the main blocker is no longer documentation ambiguity. The remaining blocker is missing runtime evidence.
\begin{itemize}
\item The canonical repo path is now clear.
\item The frozen reference window and operating mode are already documented.
\item The current workspace still lacks materialized later-phase outputs for alerts, analyst feedback, validation, backtesting, and modern ML evaluation.
\item The current committed Phase 6 trainer is still a linear starter ranker, while the SRS requires one LightGBM or CatBoost ranker evaluated against wallet-unaware baselines.
\item The current workspace still cannot defend one fully populated replay-to-alert-to-evaluation evidence packet end to end.
\end{itemize}

Phase 9 therefore exists to close the exact gap between:
\begin{itemize}
\item a repo that is architecturally coherent and honestly documented, and
\item a repo that is materially strong enough to claim SRS-complete v1 status.
\end{itemize}

\section*{Owned Deliverables (Synthesized From SRS + Phase 8 Findings)}
\begin{enumerate}
\item Materialize one canonical reference window from raw archive through Phase 3 candidate generation, Phase 4 evidence and alerting, Phase 5 validation/backtesting, and Phase 6 shadow ML evaluation.
\item Produce persisted Phase 4 evidence-query, evidence-snapshot, alert, delivery-attempt, and analyst-feedback rows tied to the chosen reference window.
\item Produce Phase 5 replay, holdout-validation, and conservative paper-trading artifacts under \texttt{reports/phase5/} and the corresponding database summary rows.
\item Upgrade Phase 6 from the current linear starter ranker to at least one SRS-compliant LightGBM or CatBoost ranker evaluated against the required wallet-unaware baselines.
\item Produce calibration outputs, severity-threshold recommendations, and model-card evidence for the promoted Phase 6 shadow model candidate.
\item Consolidate the still-active historical runbook path for Phase 5 and Phase 6 into clear single-owner operator guidance where needed.
\item Regenerate the Phase 8 Task 2 through Task 5 closeout artifacts after runtime evidence is materialized, so the final SRS-completion answer reflects actual populated evidence rather than only frozen provenance.
\item Write one final single-owner memo stating whether the project is now SRS-complete v1 or which exact blocker still remains active.
\end{enumerate}

\section*{Phase 9 Exit Criteria}
\begin{itemize}
\item One exact historical window can be defended from raw input through alert, validation, and ML-shadow evidence with saved artifacts and non-zero persisted later-phase rows.
\item Phase 4 has real evidence and alert artifacts that are replay-linked and reviewable.
\item Phase 5 has at least one conservative backtest and one paper-trading evaluation that can be cited honestly.
\item Phase 6 has at least one LightGBM or CatBoost ranker evaluated against wallet-unaware baselines with saved calibration outputs.
\item The canonical v1 operating mode remains traceable as \texttt{rule\_based\_plus\_shadow\_ml} unless a separate later promotion memo says otherwise.
\item The final Phase 8 closeout answer can be refreshed using materialized evidence rather than only structure and policy.
\end{itemize}

\section*{Locked Scope Decisions}
\begin{itemize}
\item Phase 9 is an evidence-completion phase, not a new architecture rewrite.
\item Canonical v1 remains local-first and \texttt{rule\_based\_plus\_shadow\_ml} during this phase.
\item Phase 9 must prioritize one or a small number of exact reference windows with saved hashes and rerunnable commands over broad but weak anecdotal coverage.
\item Phase 7 research artifacts remain research-only unless a separate explicit promotion decision is written after stronger Phase 6 evidence exists.
\item If later-phase tables remain empty, Phase 9 must say so plainly; documentation-only claims do not count as completion.
\item Placeholder or disabled evidence-provider paths do not count as strong final Phase 4 validation. Phase 9 must either materialize real provider-backed evidence behavior or record that the SRS evidence requirement remains partially unmet.
\item Live capital deployment, autonomous execution, cloud migration, and HA redesign remain out of scope.
\end{itemize}

\section*{Concrete Artifacts Required}
\begin{longtable}{p{0.24\linewidth}p{0.36\linewidth}p{0.26\linewidth}}
\textbf{Workstream} & \textbf{Artifact} & \textbf{Done Condition} \\
Reference window materialization & One replay-linked end-to-end evidence packet & Raw archive, detector-input, candidate, alert, validation, and ML-shadow outputs all exist for the same exact window \\
Phase 4 runtime evidence & Persisted alert/evidence/analyst artifacts plus a compact review memo & The repo can show real later-phase rows rather than empty tables and planning-only docs \\
Phase 5 validation & Replay report, holdout report, backtest report, and summary tables & Historical evaluation is point-in-time honest and materially populated \\
Phase 6 completion & LightGBM or CatBoost model artifact, baseline comparison, calibration outputs, and model card & The SRS Phase 6 model requirement is met at shadow-evaluation level \\
Runbook consolidation & Single-owner operator path for replay, validation, training, and rollback & A reviewer no longer has to infer ownership from historical person-labeled runbooks \\
Closeout refresh & Updated Phase 8 generated manifests and final completion memo & The v1-complete answer is based on refreshed evidence, not stale empty-state review \\
\end{longtable}

\section*{Canonical Phase 9 Workflow}
\begin{enumerate}
\item Choose the exact reference window or windows that will anchor the final SRS completion claim.
\item Rebuild or republish the relevant replay inputs and verify that Phase 3 emits reproducible candidates for the same window.
\item Run Phase 4 evidence, alerting, delivery, and analyst workflow so the chosen window has materialized later-phase runtime evidence.
\item Run Phase 5 replay validation, holdouts, and conservative paper-trading on the same reference path.
\item Train and evaluate one SRS-compliant boosted-tree ranker in Phase 6 shadow mode and persist the evaluation artifacts.
\item Refresh the Phase 8 reference-path, metrics, operating-mode, and final-closeout outputs against the newly materialized evidence.
\item Write the final single-owner completion memo.
\end{enumerate}

\section*{Concrete Execution Sequence}
\textbf{Block 1: Reference-window preparation}
\begin{itemize}
\item Reuse the strongest exact window already frozen by Phase 8 unless a stronger fully populated window is now available.
\item Verify raw archive partitions, detector-input manifests, and replay prerequisites before later-phase runs begin.
\item Freeze the exact command path and output directories that Phase 9 will treat as canonical.
\end{itemize}

\textbf{Block 2: Candidate-to-alert materialization}
\begin{itemize}
\item Ensure Phase 3 candidate outputs are present and linked to the chosen window.
\item Run the Phase 4 pipeline so evidence queries, evidence snapshots, alerts, delivery attempts, and analyst actions are all persisted.
\item Archive one concise review packet showing what triggered, what evidence existed, what was delivered, and how an analyst responded.
\end{itemize}

\textbf{Block 3: Historical validation and conservative evaluation}
\begin{itemize}
\item Run the Phase 5 replay bundle, holdout evaluation, and conservative paper-trading workflow on the same reference path.
\item Save the resulting reports under \texttt{reports/phase5/} and confirm their matching summary rows exist in durable tables.
\item Reject any result that depends on future leakage, optimistic fills, or undocumented manual cleanup.
\end{itemize}

\textbf{Block 4: SRS-compliant Phase 6 model evidence}
\begin{itemize}
\item Build or extend the training dataset from replay-derived Phase 5 outputs.
\item Train at least one LightGBM or CatBoost ranker and compare it against the required wallet-unaware baselines.
\item Persist calibration profiles, threshold recommendations, model-card outputs, registry metadata, and shadow-score evidence.
\item Keep the canonical operating mode rule-based plus shadow ML unless a separate later memo justifies promotion.
\end{itemize}

\textbf{Block 5: Single-owner runbook and closeout refresh}
\begin{itemize}
\item Replace the most important historical person-labeled operator instructions with clear single-owner guidance.
\item Regenerate the Phase 8 Task 2 through Task 5 outputs after evidence is materialized.
\item Write one final memo saying either ``SRS-complete v1'' or naming the exact unresolved blocker still preventing that claim.
\end{itemize}

\section*{Expected Areas To Touch}
\begin{itemize}
\item \texttt{Documentation/phases/phase9.tex}
\item \texttt{Documentation/phases/phase8\_reference\_path.tex}
\item \texttt{Documentation/phases/phase8\_metrics\_review.tex}
\item \texttt{Documentation/phases/phase8\_final\_closeout.tex}
\item \texttt{database/PHASE4\_LOCAL\_RUNBOOK.md}
\item \texttt{database/PHASE5\_PERSON1\_RUNBOOK.md} and \texttt{database/PHASE6\_PERSON1\_RUNBOOK.md} / \texttt{database/PHASE6\_PERSON2\_RUNBOOK.md} until single-owner replacements exist
\item \texttt{phase5/}, \texttt{phase6/}, and their runner entrypoints
\item generated outputs under \texttt{reports/phase5/}, \texttt{reports/phase6/}, and \texttt{reports/phase8/}
\end{itemize}

\section*{Non-Goals}
\begin{itemize}
\item No new Phase 7 research branch as part of Phase 9 completion work.
\item No automatic promotion of ML into authoritative alert gating.
\item No attempt to hide empty or weak runtime evidence behind stronger wording.
\item No return to split-by-person planning for this phase.
\end{itemize}

\section*{Phase 9 Readiness Standard}
Phase 9 is complete when a single owner can point to one exact replay-linked window and defend the entire later-phase story with materially populated evidence: candidate generation, alerting, analyst workflow, replay validation, conservative backtesting, and SRS-compliant shadow ML evaluation. At that point the project is no longer merely well-structured and honestly documented. It becomes materially strong enough to answer the SRS v1-complete question with evidence rather than with caveats.

\end{document}
