\documentclass{article}
\usepackage[margin=1in]{geometry}
\begin{document}

\section*{Phase 11 Current State Memo}

\textbf{Date:} May 15, 2026\\
\textbf{Source of truth:} \texttt{run\_runtime.py --check-only}, \texttt{run\_phase11\_runtime\_proof.py --json}, \texttt{run\_runtime\_status.py --recent-hours 24}, \texttt{run\_phase11\_status.py --recent-hours 24 --json}, and \texttt{run\_runtime\_storage\_status.py --json}.\\
\textbf{Purpose:} Record the truthful current runtime state after the Phase 11 remediation pass and the May 15 bounded runtime proof.

\section*{Configured Runtime Story}
The configured canonical local runtime profile is now \texttt{alert\_live}. In plain terms:
\begin{itemize}
\item Phase 3 live detection is required for the canonical runtime path.
\item Phase 4 is the canonical downstream live path.
\item Phase 6 remains a shadow-only extension and is \textbf{not} part of the default local runtime, but it now has a bounded shadow-score proof row.
\end{itemize}

\section*{Observed Runtime Truth On May 15, 2026}
The truthful observed state has improved since the earlier May 13 inspection:
\begin{itemize}
\item recent Phase 3 checkpoint activity is now non-zero in the inspected 24-hour window,
\item recent Phase 3 candidate activity is now non-zero in the inspected 24-hour window,
\item recent Phase 4 evidence, alert, and local delivery activity is now non-zero in the inspected 24-hour window,
\item recent live Phase 6 shadow-score activity is now non-zero in the inspected 24-hour window,
\item the observed recent runtime profile now classifies as \texttt{shadow\_live}.
\end{itemize}

\section*{Bounded Proof Truth}
The May 15 proof used \texttt{run\_phase11\_runtime\_proof.py}. Because the historical April seed detector-input partitions expected by that script were missing locally, the proof used an explicitly labeled \texttt{synthetic\_detector\_input\_fallback}. This proves that the current Phase 3 and Phase 4 runtime pipeline can produce:
\begin{itemize}
\item durable detector checkpoints,
\item a signal candidate,
\item Phase 4 evidence queries and evidence snapshot,
\item an alert,
\item a local no-op delivery attempt.
\end{itemize}

It does \textbf{not} prove that the deleted April archives were restored, and it should not be described as an organic sustained live-market run. After pausing the background collector to clear SQLite write contention, a bounded Phase 6 shadow-scoring pass also succeeded. The honest claim is: \textbf{bounded Phase 11 end-to-end proof succeeded through Phase 4, with one current Phase 6 shadow-score row; sustained live operation remains the next operational hardening step if more time is available.}

\section*{Storage Truth}
As of May 15, 2026, the local runtime uses \texttt{.env.runtime} with a reduced proof-time free-percent floor. After the SSD backup and local archive prune, storage status is \texttt{warning} rather than \texttt{blocked}: local free headroom is now about \texttt{132G}, but managed repo storage is still just above the warning threshold because the canonical SQLite DB is about \texttt{27G}. This is acceptable for bounded proof work and short organic reruns.

The attached SSD now contains a verified Phase 11 closeout backup of the SQLite DB, reports, and Phase 11 docs, plus copied \texttt{data/raw} and \texttt{data/detector\_input} archive trees. The local \texttt{data/raw} and \texttt{data/detector\_input} archive copies were pruned after the SSD copy was confirmed, then recreated as empty runtime directories for future collection.

\section*{Secret Handling Truth}
The canonical workflow no longer needs repo-local plaintext secret dependence. The intended posture is:
\begin{itemize}
\item keep non-secret toggles in \texttt{.env.runtime},
\item keep secrets in OS environment variables, a keychain-backed loader, or the repo-ignored \texttt{.env.runtime.secrets} file,
\item treat legacy \texttt{.env} loading as a compatibility fallback rather than the recommended path.
\end{itemize}

\section*{Bottom Line}
Phase 11 has made the runtime more truthful and safer:
\begin{itemize}
\item startup is canonical,
\item detector state is stricter,
\item Phase 4 and Phase 6 status is explicit,
\item replay and storage posture are now inspectable,
\item secret handling guidance is safer.
\end{itemize}

What it has now proven is a bounded end-to-end \texttt{alert\_live} pipeline path plus a bounded \texttt{shadow\_live} Phase 6 scoring extension. What it has \textbf{not} yet proven is a long, sustained, organic live-market run under relaxed storage pressure.

\end{document}
