\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{longtable}
\begin{document}

\section*{Phase 8 Task 3 - Canonical v1 Operating Mode Decision}

\textbf{Source of truth:} \texttt{Documentation/SRS.tex}, the generated operating-mode manifest under \texttt{reports/phase8/operating\_mode/}, and the committed Phase 4 through Phase 7 implementation referenced below.\\
\textbf{Task goal:} Make a formal decision on what counts as the real v1 system and classify which Phase 7 outputs are research-only versus allowed to influence the canonical v1 story.

\section*{Formal Decision}
\textbf{Canonical v1 operating mode:} \texttt{rule\_based\_plus\_shadow\_ml}

This means:
\begin{itemize}
\item deterministic Phase 3 candidate generation remains authoritative,
\item Phase 4 alerting, evidence, suppression, and analyst workflow remain authoritative,
\item Phase 5 replay, holdout evaluation, and conservative paper-trading remain the required validation layer,
\item Phase 6 ML infrastructure remains active in shadow mode for scoring, logging, comparison, calibration, and operator learning,
\item but ML does \textbf{not} become the authoritative alert-decision path for canonical v1.
\end{itemize}

\section*{Modes Considered}
\begin{longtable}{p{0.24\linewidth}p{0.18\linewidth}p{0.44\linewidth}}
\textbf{Mode} & \textbf{Decision} & \textbf{Reason} \\
\texttt{rule\_based\_only} & Rejected & Too weak for the actual repo state because the committed Phase 6 registry, shadow-scoring, and evaluation plumbing should remain active as part of the v1 operational story. \\
\texttt{rule\_based\_plus\_shadow\_ml} & Accepted & Best fit for both the SRS and the committed implementation: the system keeps rule-based authority while ML remains traceable, comparable, and safely reversible. \\
\texttt{ml\_backed\_ranking\_with\_rollback} & Rejected for canonical v1 & Not justified by the current repo state. Phase 6 is shadow-first by design, the committed trainer is still a linear starter ranker, and this workspace does not contain a materialized evidence packet strong enough to promote ML into authority. \\
\end{longtable}

\section*{Primary Rationale}
\begin{enumerate}
\item The SRS definition of v1 complete requires a ranker to be \textbf{evaluated} against baselines, not automatically promoted into the authoritative alert path.
\item The SRS Phase 6 plan explicitly says to integrate the ranker in \textbf{shadow mode first}.
\item The canonical Phase 4 single-owner plan keeps the alert loop rule-based and operator-facing before any ML promotion.
\item The committed Phase 6 implementation is still a \textbf{linear starter ranker}. Its own reporting code says the thresholds should be treated as \textbf{shadow-only recommendations} and that it is not yet the final boosted-tree model promised by the full Phase 6 scope.
\item Phase 7 is explicitly framed as \textbf{advanced research after v1 stability}. It should therefore refine governance, observability, and thesis claims, but it must not silently redefine the canonical v1 operating mode.
\end{enumerate}

\section*{What Counts as the Real v1 System}
\textbf{Authoritative v1 path}
\begin{itemize}
\item Phase 3 deterministic candidate engine
\item Phase 4 evidence enrichment and explainable alert workflow
\item Phase 4 suppression and analyst-feedback path
\item Phase 5 replay, holdouts, and conservative paper-trading evaluation
\end{itemize}

\textbf{Shadow-only v1 path}
\begin{itemize}
\item Phase 6 feature materialization for training and inference
\item Phase 6 model registry and activation/retirement controls
\item Phase 6 shadow scoring and score logging
\item Phase 6 evaluation and calibration reports
\end{itemize}

\textbf{Operational rollback rule}
\begin{itemize}
\item If ML plumbing is disabled or a shadow model is retired, the authoritative rule-based alert path still works unchanged.
\item Canonical v1 must never require a model artifact to keep the base alert loop alive.
\end{itemize}

\section*{Phase 7 Classification}
\textbf{Research-only for canonical v1}
\begin{itemize}
\item graph-derived feature families,
\item graph-aware advanced ranker artifacts,
\item Hawkes / TCN style experiments,
\item ablation tables and thesis-quality figures as headline model claims,
\item Phase 7 research packages as deployment authority.
\end{itemize}

\textbf{Allowed to influence the canonical v1 story, but not the decision logic}
\begin{itemize}
\item observability / Goodhart warnings that constrain how much operator trust should be placed in visible metrics,
\item strict-holdout promotion discipline when comparing advanced experiments against the Phase 6 baseline,
\item scale, cost, storage, restore, and long-run dashboard guidance from the Phase 7 operational track,
\item reproducibility packaging standards for thesis, demo, or defense artifacts.
\end{itemize}

\textbf{Explicit non-promotion rule}
\begin{itemize}
\item No Phase 7 model artifact changes canonical v1 alert generation merely because it exists in the repo.
\item Any future promotion beyond shadow mode would require a separate explicit decision with stronger operational evidence than is available in this workspace snapshot.
\end{itemize}

\section*{Implications for Phase 8 Closeout}
\begin{itemize}
\item The final v1 story should describe the project as a \textbf{rule-based alerting system with shadow ML evaluation}, not as a fully ML-driven ranking system.
\item Phase 6 artifacts are part of canonical v1 because they provide traceable shadow scoring, registry control, and evaluation evidence.
\item Phase 7 artifacts remain valuable, but mainly as research, governance, and observability inputs rather than live decision authority.
\item README, phase docs, and closeout material should avoid language implying that ML already owns alert gating in canonical v1.
\end{itemize}

\section*{Generated Policy Artifact}
Task 3 also writes a machine-readable policy record and a markdown summary:
\begin{itemize}
\item \texttt{reports/phase8/operating\_mode/phase8\_v1\_operating\_mode\_manifest.json}
\item \texttt{reports/phase8/operating\_mode/phase8\_v1\_operating\_mode\_summary.md}
\end{itemize}

These files record the operating-mode decision, rejected alternatives, supporting evidence paths and hashes, and the formal classification of Phase 7 outputs.

\end{document}
