\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{longtable}
\begin{document}

\section*{Phase 1 Validation Contract - Person 2}

\textbf{Phase:} 1\\
\textbf{Owner:} Person 2 (Person B)\\
\textbf{Source of truth:} \texttt{Documentation/SRS.tex}, Section 11.4, ``Phase 1: Fix Ingestion Correctness''\\
\textbf{Machine-readable companion:} \texttt{config/phase1\_validation.yaml}

\section*{Purpose}

This contract defines the first canonical validation layer for wallet-aware
trade correctness. It is the shared reference for:
\begin{itemize}
\item field-level expectations for Phase 1 trade records,
\item approved-universe validation scope,
\item candidate-review output validation for excluded but finance-relevant
events,
\item interface compatibility with market descriptors and condition-based trade
ingestion,
\item validation thresholds,
\item deterministic semantics for \texttt{first\_seen\_at}, fresh-wallet status,
and trade-to-market episode linkage.
\end{itemize}

\section*{Scope}

Phase 1 validation is intentionally scoped to the approved target-market
universe. It does not attempt to validate the full Polymarket exchange.
All quality checks, QA samples, and signoff metrics must be computed only over
the approved market set unless a specific leakage check is being run.

\section*{Dependencies On Person 1 Outputs}

This contract assumes Person 1 will provide:
\begin{itemize}
\item final universe-policy behavior and config schema,
\item stable event tag-id storage in synced event metadata,
\item market descriptors carrying \texttt{market\_id}, \texttt{condition\_id},
\texttt{yes\_token\_id}, \texttt{no\_token\_id}, \texttt{event\_id}, and
\texttt{tier},
\item the canonical trade field map for new ingestion columns,
\item source-priority and dedupe rules across WebSocket, REST, and backfill,
\item condition-id-based trade ingestion for REST and backfill paths,
\item evidence that both YES and NO assets are being ingested.
\end{itemize}

If any dependency is missing, validators must fail explicitly with a clear
reason rather than silently skipping checks.

\section*{Approved Market Universe Contract}

\begin{itemize}
\item Validation inputs must be filtered through the approved universe-policy
selector.
\item Leakage outside the approved universe is a tracked defect.
\item Universe-selection rules must be versioned so repeated validation runs are
reproducible.
\item Report outputs must state which selector version and universe-policy
inputs were used.
\item Stable tag IDs must be preferred over free-text tag labels whenever they
are available.
\item Candidate-review output for excluded but finance-relevant events is part
of the Phase 1 validation surface and must be reviewed alongside the approved
universe.
\end{itemize}

\section*{Interface Compatibility Contract}

\subsection*{Event Metadata}
\begin{itemize}
\item Event metadata must store stable tag IDs alongside tag labels.
\item Validation should prefer tag-ID-based policy matching and fall back to tag
labels only if stable IDs are unavailable.
\end{itemize}

\subsection*{Market Descriptors}
\begin{itemize}
\item Runtime collector interfaces are expected to move from one-token maps to
market descriptors.
\item Validation must assume market descriptors expose
\texttt{market\_id}, \texttt{condition\_id}, \texttt{yes\_token\_id},
\texttt{no\_token\_id}, \texttt{event\_id}, and \texttt{tier}.
\item Both-asset coverage checks must validate YES and NO coverage at the parent
market level rather than assuming YES-token-only routing.
\end{itemize}

\section*{Canonical Wallet-Aware Trade Entity}

The canonical Phase 1 trade entity is the minimum normalized record required to
judge whether wallet-aware ingestion is semantically usable downstream.

\begin{longtable}{p{0.20\linewidth}p{0.14\linewidth}p{0.12\linewidth}p{0.19\linewidth}p{0.25\linewidth}}
\textbf{Field} & \textbf{Type} & \textbf{Nullable} & \textbf{Severity} & \textbf{Rule} \\
\texttt{trade\_id} & string & no & error & Must uniquely identify a canonical trade record \\
\texttt{market\_id} & string & no & error & Must map to an approved market when validation is scoped \\
\texttt{condition\_id} & string & no & error & Must be populated when the market has a valid condition identifier \\
\texttt{asset\_id} & string & no & error & Must identify the traded YES/NO asset \\
\texttt{proxy\_wallet} & string & yes & warn & Null-rate is monitored and bounded by threshold \\
\texttt{transaction\_hash} & string & yes & warn & Null-rate is monitored and bounded by threshold \\
\texttt{outcome\_side} & enum & no & error & Must be deterministic and restricted to \texttt{YES}/\texttt{NO} \\
\texttt{price} & float & no & error & Must be numeric and represent the unit execution price \\
\texttt{size} & float & no & error & Must be numeric and positive \\
\texttt{usdc\_notional} & float & no & error & Must be numeric and consistent with price/size rules \\
\texttt{dedupe\_key} & string & no & error & Must capture transaction-hash-based or fallback economic-trade identity \\
\texttt{source\_priority} & integer & no & error & Must encode canonical source precedence for downstream duplicate resolution \\
\texttt{trade\_time} & timestamp & no & error & Must represent provider event time when available \\
\texttt{source} & enum & no & error & Must identify ingestion origin for dedupe and QA \\
\end{longtable}

\section*{Validation Checks}

\subsection*{1. Both-Side Asset Coverage}
\begin{itemize}
\item Validate that approved markets expose observable activity for both YES and
NO assets.
\item Report coverage counts and ratios at market, source, and aggregate levels.
\item Record failing markets with reason codes for handoff to Person 1.
\end{itemize}

\subsection*{2. Universe Leakage And Candidate Review}
\begin{itemize}
\item Validate that expensive collection only lands for approved-universe
markets.
\item Validate that excluded but finance-relevant active events are surfaced in
the candidate-review output rather than silently ignored.
\item Verify candidate-review output columns, reproducibility, and reason codes.
\end{itemize}

\subsection*{3. Duplicate Trade Inflation And Canonical Resolution}
\begin{itemize}
\item Measure duplicate inflation across WebSocket, REST, and backfill paths.
\item Use \texttt{transaction\_hash} as the strongest dedupe key when present.
\item Fall back to a deterministic key built from \texttt{condition\_id},
\texttt{asset\_id}, \texttt{outcome\_side}, price, size, and normalized event
time.
\item Validate that \texttt{dedupe\_key} and \texttt{source\_priority} are
populated and coherent with the source-priority policy.
\item Report both raw duplicate counts and inflation ratios.
\end{itemize}

\subsection*{4. Wallet Field Null-Rate}
\begin{itemize}
\item Track null-rate separately for each wallet-linked field.
\item Segment results by source and market group where needed.
\item Treat threshold breaches as validation failures even if schema allows
nulls.
\end{itemize}

\subsection*{5. Condition-ID Population}
\begin{itemize}
\item Measure the share of approved-universe trades with populated
\texttt{condition\_id}.
\item Report the population rate overall and by source.
\item Highlight mismatches between market metadata and trade records.
\end{itemize}

\subsection*{6. Asset And Outcome Correctness}
\begin{itemize}
\item Validate that \texttt{asset\_id} is populated and maps to the YES or NO
token on the referenced market descriptor.
\item Validate that \texttt{outcome\_side} is populated and restricted to
\texttt{YES}/\texttt{NO}.
\item Validate that condition-id-based trade ingestion lands trades against the
correct market descriptor.
\end{itemize}

\section*{Deterministic Semantics}

\subsection*{\texttt{first\_seen\_at}}

\texttt{first\_seen\_at} means the earliest timestamp observed in our archive for
the wallet or entity being evaluated. It does not claim to be the earliest
platform existence time. The first executable implementation must:
\begin{itemize}
\item derive \texttt{first\_seen\_at} as the minimum observed
\texttt{trade\_time} per non-blank \texttt{proxy\_wallet},
\item preserve provenance as archive-derived rather than platform-derived,
\item fail explicitly if the required entity or event-time fields are missing.
\end{itemize}

\subsection*{Fresh-Wallet Flag}

Fresh-wallet status is computed, not absolute. The first implementation must be
based on:
\begin{itemize}
\item archive-backed \texttt{first\_seen\_at},
\item known trading footprint,
\item profile-age evidence when available,
\item a confidence flag that surfaces known archive gaps or downtime.
\end{itemize}

The initial deterministic rule will classify a wallet as fresh when its
archive-derived age and known trade footprint both remain below configured
thresholds. Confidence is downgraded when profile-age evidence is unavailable or
event-time evidence is incomplete.

\subsection*{Trade-To-Market Episode Linkage}

Episode linkage rules must be deterministic and executable in validation
queries. At minimum, the linkage contract must specify:
\begin{itemize}
\item which market or condition identifiers drive joins,
\item which event-time field anchors ordering,
\item how both-side asset activity is associated to one market episode,
\item how ambiguous or unmatched trades are classified.
\end{itemize}

The first executable implementation will:
\begin{itemize}
\item partition trades by \texttt{market\_id} and \texttt{condition\_id},
\item order trades by \texttt{trade\_time},
\item start a new episode whenever the configured inactivity gap is exceeded,
\item attach YES and NO side activity to the same episode when they fall inside
the same market-condition time window,
\item classify trades with missing linkage keys as unresolved and report them.
\end{itemize}

\section*{Thresholds And Outputs}

Threshold values are stored in the machine-readable companion configuration so
they can change without rewriting validation code. Every validation run must
emit:
\begin{itemize}
\item a run timestamp,
\item configuration version,
\item selector version or universe-policy source,
\item aggregate metrics,
\item failing-record samples,
\item pass/warn/fail status by check.
\end{itemize}

\section*{QA Sampling Protocol}

Manual QA must review at least 20 trade episodes. The review sheet must capture:
\begin{itemize}
\item episode identifier,
\item market identifier,
\item observed YES/NO coverage,
\item wallet field completeness,
\item condition-id completeness,
\item duplicate observations,
\item candidate-review cross-check status when applicable,
\item pass/fail decision,
\item notes and failure taxonomy.
\end{itemize}

\section*{Gate 1 Acceptance Criteria}

\begin{itemize}
\item The validation contract is versioned and stored in-repo.
\item Thresholds are versioned and machine-readable.
\item Validators can consume the contract without hard-coded assumptions.
\item QA artifacts are ready before the full validation logic lands.
\item Failures are explainable and reproducible for Person 1 handoff.
\end{itemize}

\end{document}
