\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{longtable}
\begin{document}

\textbf{Legacy note:} This split-by-person draft is superseded by the canonical single-owner Phase 2 document at \texttt{Documentation/phases/phase2.tex}.\\

\section*{Phase 2 Plan - Person 2 (Person B)}

\textbf{Source of truth:} \texttt{Documentation/SRS.tex}, Section 11.4, ``Phase 2: Build the Durable Data Plane''.
\textbf{Interpretation note:} Phase 2 for Person 2 is about proving that the new durable local data plane is actually usable. The replay path, point-in-time contracts, and reconstruction proof are the acceptance criteria for the storage and transport work.
\textbf{Implementation note:} Validation remains scoped to the approved universe and the archived raw data produced by Phase 2. Person 2 is not re-litigating Phase 1 selection policy here; the job is to prove replayability, ordering correctness, and point-in-time state reconstruction on the local-first canonical stack.

\textbf{Phase duration:} 2-3 weeks\\
\textbf{Phase goal:} Define replay contracts and prove a historical window can be reconstructed from durable archives.

\section*{Owned Deliverables (From SRS)}
\begin{enumerate}
\item Define the normalized envelope contract consumed by the detector.
\item Build replay-validation tooling that:
\begin{itemize}
\item replays a chosen archive window,
\item compares replayed counts to original counts,
\item verifies ordering and timestamp behavior.
\end{itemize}
\item Define the point-in-time contract for profiles, activity, and evidence snapshots.
\item Produce one replay case study proving a one-hour window can be reconstructed.
\end{enumerate}

\section*{Locked Implementation Decisions}
\begin{itemize}
\item Replay validation is based on immutable raw archives and manifest metadata, not on trusting the live operational database alone.
\item The detector-facing normalized envelope contract must preserve source provenance, schema version, capture time, event ordering metadata, and identifiers needed for market, asset, wallet, and episode reconstruction.
\item Point-in-time outputs are archive-relative snapshots and must be derivable from replayed inputs without consulting future state.
\item Replay proof must verify both count parity and ordering semantics, not just that some rows were reproduced.
\item Gate 2 success requires a reconstruction proof over a bounded historical window that another teammate can rerun deterministically.
\end{itemize}

\section*{Concrete Execution Breakdown}
\begin{longtable}{p{0.28\linewidth}p{0.32\linewidth}p{0.30\linewidth}}
\textbf{Work Item} & \textbf{Artifact} & \textbf{Done Condition} \\
Normalized envelope contract & Detector-facing contract spec and examples & Every downstream-required field is typed, versioned, and mapped back to raw provenance \\
Replay-validation tooling & Replay runner plus parity and ordering checks & A chosen archive window can be replayed and compared against original counts and ordering expectations \\
Point-in-time snapshot contract & Snapshot spec for profiles, activity, and evidence & Snapshot semantics are deterministic and do not rely on future information leakage \\
Replay case study & Gate 2 proof package for a one-hour window & The team can rerun one bounded historical reconstruction and reproduce the same evidence \\
\end{longtable}

\section*{Execution Sequence (No Day Timeline)}
\textbf{Block 1: Contract definition}
\begin{itemize}
\item Define the normalized envelope schema expected by the detector and map each field back to raw archive provenance.
\item Review Person 1's raw-envelope and archive conventions to ensure replay assumptions are explicit rather than implied.
\item Freeze contract versioning rules so replay tooling can handle schema evolution safely.
\end{itemize}

\textbf{Block 2: Replay tooling and parity checks}
\begin{itemize}
\item Build tooling that reads one archive window from the local durable archive, replays envelopes in deterministic order, and materializes validation outputs.
\item Compare replayed counts to original manifests and operational outputs for the same window.
\item Verify ordering, event-time behavior, and duplicate-handling semantics, especially for wallet and episode-sensitive records.
\item Produce replay diagnostics that explain count deltas or ordering drift with concrete reason codes.
\end{itemize}

\textbf{Block 3: Point-in-time state definition}
\begin{itemize}
\item Define point-in-time contracts for wallet profiles, market activity, and evidence snapshots used by later detector phases.
\item Confirm that each snapshot can be rebuilt from replayed envelopes without leaking future knowledge.
\item Raise any provenance gaps, missing fields, or schema-version edge cases to Person 1 before Gate 2 signoff.
\end{itemize}

\textbf{Block 4: Replay proof and signoff pack}
\begin{itemize}
\item Produce a one-hour replay case study with exact archive inputs, replay procedure, and expected outputs.
\item Document parity results, ordering results, and any reconstruction caveats.
\item Assemble the Gate 2 evidence packet so the replay proof can be rerun by either teammate.
\end{itemize}

\section*{Handoffs to Person 1}
\begin{itemize}
\item Detector-facing normalized envelope contract and any required field corrections.
\item Replay-tool findings on missing provenance, ordering drift, or manifest mismatch.
\item Point-in-time contract requirements for profiles, activity, and evidence snapshots.
\item Concrete archive windows used for replay proof and their reproducibility status.
\item Gate 2 parity and ordering evidence for shared signoff.
\item Any raw-capture or local-PostgreSQL-write gaps that block deterministic reconstruction.
\end{itemize}

\section*{Gate 2 Checklist (Person 2 Ownership)}
\begin{itemize}
\item Normalized envelope contract is versioned and mapped to raw provenance.
\item Replay tooling can reconstruct a bounded archive window deterministically.
\item Replayed counts match expected counts or have explicit investigated deltas.
\item Ordering and timestamp behavior are validated and documented.
\item Point-in-time snapshot contracts are deterministic and future-safe.
\item One one-hour replay proof is complete and rerunnable by the team.
\end{itemize}

\end{document}
