\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{longtable}
\begin{document}

\section*{Phase 1 Plan - Person 2 (Person B)}

\textbf{Source of truth:} \texttt{Documentation/SRS.tex}, Section 11.4, ``Phase 1: Fix Ingestion Correctness''.
\textbf{Interpretation note:} Phase 1 does not mean validating the full Polymarket exchange. Validation is scoped to the approved target-market universe so analysis stays compute-efficient and focused on markets that matter.
\textbf{Implementation note:} Full event and market metadata sync still runs across the full exchange. Validation targets the approved high-resolution universe plus the candidate-review output for excluded but review-worthy events.

\textbf{Phase duration:} 1-2 weeks\\
\textbf{Phase goal:} Validate and operationalize wallet-aware trade correctness.

\section*{Owned Deliverables (From SRS)}
\begin{enumerate}
\item Write canonical entity and field validation spec for wallet-aware trades.
\item Build validation scripts for:
\begin{itemize}
\item both-side asset coverage
\item duplicate trade inflation
\item null-rate of wallet fields
\item \texttt{condition\_id} population rate
\end{itemize}
\item Define first version of:
\begin{itemize}
\item \texttt{first\_seen\_at}
\item fresh-wallet flag logic
\item trade-to-market episode linkage rules
\end{itemize}
\item Produce QA sample review over at least 20 manually inspected trade episodes.
\end{enumerate}

\section*{Locked Implementation Decisions}
\begin{itemize}
\item Coverage policy is \textbf{Broad Cross-Domain}, not strict finance-only.
\item Candidate-review guardrail is enabled and must be validated for leakage and relevance.
\item Both YES and NO assets are collected for WebSocket, order-book, and price coverage.
\item Trade ingestion uses \texttt{condition\_id} and stores returned \texttt{asset}, \texttt{outcome}, \texttt{proxyWallet}, and \texttt{transactionHash}.
\item Fresh-wallet validation is archive-relative with provenance, not platform-absolute.
\end{itemize}

\section*{Concrete Execution Breakdown}
\begin{longtable}{p{0.28\linewidth}p{0.32\linewidth}p{0.30\linewidth}}
\textbf{Work Item} & \textbf{Artifact} & \textbf{Done Condition} \\
Canonical validation spec & Field-level data contract document & Every required Phase 1 field has type, nullability, and semantic rule \\
Universe-scoped coverage and inflation checks & Validation SQL/script suite & Only approved markets are measured, and both-side coverage plus duplicate inflation are reported for that universe \\
Episode semantics & Spec for \texttt{first\_seen\_at}, fresh-wallet, linkage & Rules are deterministic, archive-relative, and executable in validation queries \\
Manual QA review & Reviewed sample sheet (>=20 episodes) & QA findings include pass/fail and failure pattern taxonomy \\
\end{longtable}

\section*{Execution Sequence (No Day Timeline)}
\textbf{Block 1: Validation contract definition}
\begin{itemize}
\item Draft canonical wallet-aware entity/field validation spec.
\item Align schema expectations and target-universe rules with Person 1 before migration lands.
\item Finalize validation thresholds for null-rate and condition-id population.
\end{itemize}

\textbf{Block 2: Universe-scoped validation setup}
\begin{itemize}
\item Implement validation checks that confirm only approved markets are ingested.
\item Validate candidate-review output so excluded but finance-relevant events are surfaced instead of silently dropped.
\item Implement data-validation scripts for both-side coverage and duplicates within the approved universe.
\item Add checks for wallet-field null-rate, \texttt{condition\_id} population, \texttt{transaction\_hash} population, and \texttt{asset\_id} / \texttt{outcome\_side} correctness.
\item Start validation report template scoped to approved markets only.
\end{itemize}

\textbf{Block 3: Episode semantics validation}
\begin{itemize}
\item Define and test \texttt{first\_seen\_at}, fresh-wallet, and episode linkage logic.
\item Validate rule stability on rolling live windows.
\item Raise schema or ingestion mismatches to Person 1 immediately.
\end{itemize}

\textbf{Block 4: Manual QA and signoff pack}
\begin{itemize}
\item Execute manual QA review on at least 20 trade episodes.
\item Produce a concise QA report with defects and severity.
\item Prepare Gate 1 signoff package with evidence.
\end{itemize}

\section*{Handoffs to Person 1}
\begin{itemize}
\item Validation failures where excluded or nonsensical markets leaked into the ingestion set.
\item Validation failures where candidate-review events should have been surfaced but were not.
\item Validation failures with concrete failing records and reason codes.
\item Duplicate inflation and null-rate trends by source and market segment.
\item Required schema or parser corrections discovered by QA.
\item Gate 1 evidence packet for shared signoff.
\end{itemize}

\section*{Gate 1 Checklist (Person 2 Ownership)}
\begin{itemize}
\item Canonical validation spec is complete and versioned.
\item Approved-market selector behavior is validated and leakage is zero or explicitly explained.
\item Candidate-review output is populated and reviewable.
\item Automated validation scripts run and produce reproducible outputs.
\item Episode and fresh-wallet logic are deterministic.
\item Manual review of >=20 episodes is complete with findings.
\end{itemize}

\end{document}
