\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{longtable}
\begin{document}

\section*{Phase 5 Person 2 - Task 4}

\textbf{Deliverable scope:} metrics catalog and reporting package only.\\
\textbf{Binding dependencies:} Task 1 point-in-time and no-leakage rules remain mandatory; Task 2 holdout and aggregation rules remain mandatory; Task 3 simulator assumptions remain mandatory for any paper-trade metric.\\
\textbf{Implementation note:} this document defines what counts as good, weak, and bad performance, and how those results must be reported without hiding poor regimes behind pooled averages.

\section*{Purpose}

\begin{itemize}
\item Define the canonical metrics used to judge replayed candidates, alerts, lead time, and simulated trades.
\item Make reporting reusable across historical windows and holdout regimes.
\item Force every report to show both success and failure views, not just favorable headline numbers.
\end{itemize}

\section*{Metric Design Principles}

\begin{itemize}
\item All metrics are computed on units defined in Task 1:
candidate,
alert,
and paper-trade.
\item All metrics must be segmented by the holdout framework defined in Task 2:
event-family holdout,
category holdout,
and time-split holdout.
\item No metric may use post-decision information as an input feature; ex-post labels are allowed only for scoring after the unit is fully constructed.
\item Coverage-limited samples remain visible in reporting with explicit status labels:
\texttt{scored},
\texttt{descriptive\_only},
or \texttt{coverage\_insufficient}.
\item No single pooled number may stand alone as the project-wide conclusion.
\end{itemize}

\section*{Metrics Catalog}

\subsection*{1. Candidate Quality Metrics}

\textbf{Purpose}
\begin{itemize}
\item Measure whether the detector emits historically meaningful candidate episodes before alert formatting and evidence adjustment.
\end{itemize}

\begin{longtable}{p{0.28\linewidth}p{0.22\linewidth}p{0.38\linewidth}}
\textbf{Metric} & \textbf{Type} & \textbf{Definition} \\
Candidate count & descriptive & Number of candidate-eligible rows in scope \\
Candidate rate per window & descriptive & Candidate count divided by decision-time window duration \\
Distinct market count & descriptive & Number of unique \texttt{market\_id} values among candidate rows \\
Distinct event-family count & descriptive & Number of unique \texttt{event\_family\_id} values among candidate rows \\
Candidate label coverage & quality-control & Share of candidate rows with valid ex-post labels \\
Candidate resolution reach rate & success/failure & Share of candidate rows that eventually resolve with a usable label \\
Candidate precision at horizon & success & Share of labeled candidate rows meeting the pre-declared success condition at the chosen historical horizon \\
Candidate false-positive rate & failure & Share of labeled candidate rows failing the success condition \\
Candidate severity decile calibration & diagnostic & Outcome rate by candidate severity-score bucket \\
Rule-family mix & diagnostic & Distribution of triggering rule families across candidate rows \\
\end{longtable}

\textbf{Interpretation}
\begin{itemize}
\item Candidate quality is good when labeled candidate precision remains stable across holdout regimes and is not produced by one narrow event family or category.
\item Candidate quality is weak when precision collapses outside one topical domain or when severity score is not monotonic with outcome quality.
\item Candidate quality is bad when candidate volume is high but label-based success is low or concentrated in one narrow regime.
\end{itemize}

\subsection*{2. Alert Usefulness Metrics}

\textbf{Purpose}
\begin{itemize}
\item Measure whether the full alert object, including severity and evidence state at alert time, would have been historically useful to a reviewer.
\end{itemize}

\begin{longtable}{p{0.28\linewidth}p{0.22\linewidth}p{0.38\linewidth}}
\textbf{Metric} & \textbf{Type} & \textbf{Definition} \\
Alert count & descriptive & Number of alert-eligible rows in scope \\
Alert creation rate & descriptive & Alerts created per historical window or per day \\
Alert suppression rate & diagnostic & Share of alert-eligible candidates suppressed before alert creation \\
Alert label coverage & quality-control & Share of alerts with usable ex-post labels \\
Alert usefulness precision & success & Share of labeled alerts meeting the pre-declared historical usefulness rule \\
Alert non-useful rate & failure & Share of labeled alerts that do not meet the usefulness rule \\
Severity-tier precision & diagnostic & Usefulness precision by alert severity tier \\
Evidence-state breakdown & diagnostic & Usefulness precision by evidence state at alert time \\
Alert redundancy rate & failure & Share of alerts clustered within the same event family and close time window that do not add new useful signal \\
Alert concentration ratio & failure & Share of total alert count explained by the top event families or categories \\
\end{longtable}

\textbf{Interpretation}
\begin{itemize}
\item Alert usefulness is good when higher-severity alerts are more useful than lower-severity alerts and usefulness remains present across holdouts.
\item Alert usefulness is weak when severity tiers do not separate outcomes or when usefulness depends heavily on one evidence state only.
\item Alert usefulness is bad when alerts are frequent but historical usefulness is low, redundant, or highly concentrated in one regime.
\end{itemize}

\subsection*{3. Lead-Time Metrics}

\textbf{Purpose}
\begin{itemize}
\item Measure how early candidates and alerts occur relative to the eventual historical outcome or decisive market move.
\end{itemize}

\begin{longtable}{p{0.28\linewidth}p{0.22\linewidth}p{0.38\linewidth}}
\textbf{Metric} & \textbf{Type} & \textbf{Definition} \\
Median lead time to resolution & success & Median \texttt{resolution\_time - decision\_timestamp} for labeled successful rows \\
P25/P75 lead time & diagnostic & Interquartile range of lead time among successful rows \\
Short-lead alert share & failure & Share of useful alerts whose lead time falls below the minimum operational threshold \\
Near-resolution trigger share & failure & Share of candidate or alert rows generated inside the near-resolution exclusion zone \\
Lead-time by severity tier & diagnostic & Median lead time within each severity band \\
Lead-time by category & diagnostic & Median lead time by canonical category \\
Lead-time by event family & diagnostic & Median lead time by event-family holdout block \\
\end{longtable}

\textbf{Interpretation}
\begin{itemize}
\item Lead time is good when useful alerts occur early enough to matter operationally and not only minutes before resolution.
\item Lead time is weak when apparent usefulness exists but mostly arrives too late for meaningful action.
\item Lead time is bad when the system mostly triggers near resolution or after public explanation has already become obvious.
\end{itemize}

\subsection*{4. Simulated Trade Performance Metrics}

\textbf{Purpose}
\begin{itemize}
\item Measure whether alert-derived paper trades retain edge under the conservative simulator assumptions from Task 3.
\end{itemize}

\begin{longtable}{p{0.28\linewidth}p{0.22\linewidth}p{0.38\linewidth}}
\textbf{Metric} & \textbf{Type} & \textbf{Definition} \\
Trade eligibility rate & diagnostic & Share of alerts that become paper-trade eligible \\
Fill rate & diagnostic & Share of eligible alerts that actually fill under conservative execution rules \\
Skip rate by reason & failure & Distribution of deterministic skip reasons \\
Median bounded PnL & success & Median conservative PnL across filled trades \\
Mean bounded PnL & descriptive & Average conservative PnL across filled trades \\
Hit rate & success & Share of filled trades with positive bounded PnL after fees and slippage \\
Loss rate & failure & Share of filled trades with non-positive bounded PnL \\
Worst decile PnL & failure & Mean or median PnL of the worst 10\% of filled trades \\
Maximum drawdown proxy & failure & Worst cumulative decline over chronological simulated trades within a reporting block \\
PnL by severity tier & diagnostic & Trade performance by originating alert severity \\
PnL by holdout regime & diagnostic & Trade performance segmented by event-family, category, and time split \\
Holding duration distribution & diagnostic & Entry-to-exit duration summary across filled trades \\
\end{longtable}

\textbf{Interpretation}
\begin{itemize}
\item Trade performance is good when bounded PnL and hit rate remain positive under conservative assumptions across more than one holdout regime.
\item Trade performance is weak when gains appear only in one time block, one category, or one severity tier.
\item Trade performance is bad when positive results disappear after fees, slippage, or realistic skip rules are applied.
\end{itemize}

\subsection*{5. Failure Metrics And Weak-Regime Reporting}

\textbf{Purpose}
\begin{itemize}
\item Prevent optimistic summaries from hiding the regimes where the system breaks, overfires, or becomes unusable.
\end{itemize}

\begin{longtable}{p{0.28\linewidth}p{0.22\linewidth}p{0.38\linewidth}}
\textbf{Metric} & \textbf{Type} & \textbf{Definition} \\
Coverage-insufficient split count & failure & Number of holdout splits not eligible for scored reporting \\
Descriptive-only split count & failure & Number of splits that do not satisfy scoring minimums but still appear in the report ledger \\
Worst regime precision & failure & Lowest candidate or alert precision among scored holdout blocks \\
Worst regime bounded PnL & failure & Lowest filled-trade bounded PnL among scored holdout blocks \\
Top-category dependency share & failure & Share of success explained by the single strongest category \\
Top-event-family dependency share & failure & Share of success explained by the single strongest event family \\
False-positive concentration & failure & Share of negative outcomes concentrated in the worst holdout blocks \\
Skip-due-to-data rate & failure & Share of paper-trade rows skipped due to missing or insufficient market data \\
Near-resolution exclusion rate & failure & Share of alerts made non-tradable by near-resolution rules \\
Weak-regime count & failure & Number of holdout blocks that fall below the minimum acceptable threshold for key metrics \\
\end{longtable}

\textbf{Interpretation}
\begin{itemize}
\item Every final report must include a named weak-regime section.
\item If the strongest results come from one narrow regime while weak regimes dominate the rest, the project may not claim broad historical usefulness.
\item Failure metrics are first-class outputs, not appendix-only diagnostics.
\end{itemize}

\section*{Metric Eligibility Rules}

\begin{itemize}
\item Candidate metrics use only \texttt{unit\_eligibility\_candidate = true} rows.
\item Alert metrics use only \texttt{unit\_eligibility\_alert = true} rows.
\item Paper-trade metrics use only \texttt{unit\_eligibility\_paper\_trade = true} rows.
\item Label-based metrics require valid ex-post labels and sufficient coverage status under Task 2.
\item Coverage-insufficient splits are excluded from scored aggregates and retained in descriptive reporting.
\end{itemize}

\section*{Reporting Package}

\subsection*{Required Report Views}

\begin{itemize}
\item \textbf{Coverage view:} what windows, units, and holdout blocks were actually evaluable.
\item \textbf{Success view:} candidate precision, alert usefulness, lead time, and bounded trade performance in scored regimes.
\item \textbf{Failure view:} false positives, weak regimes, concentration, skip reasons, and poor trade blocks.
\item \textbf{Regime view:} event-family holdout, category holdout, and time-split comparisons side by side.
\item \textbf{Case-study pointer view:} identify strongest, weakest, and most ambiguous historical windows for later Task 5 writeups.
\end{itemize}

\subsection*{Reusable Backtesting Report Template}

\textbf{Section 1: Run Identity}
\begin{itemize}
\item validation run id
\item replay run ids or source windows
\item detector version
\item alert workflow version
\item simulator version
\item metric catalog version
\item report generation timestamp
\end{itemize}

\textbf{Section 2: Scope And Coverage}
\begin{itemize}
\item historical windows included
\item holdout regimes included
\item total candidate rows
\item total alert rows
\item total paper-trade eligible rows
\item scored split count
\item descriptive-only split count
\item coverage-insufficient split count
\item coverage reason codes
\end{itemize}

\textbf{Section 3: Candidate Quality Scorecard}
\begin{itemize}
\item candidate count
\item label coverage
\item candidate precision
\item false-positive rate
\item severity calibration summary
\item top rule-family breakdown
\item worst holdout block
\end{itemize}

\textbf{Section 4: Alert Usefulness Scorecard}
\begin{itemize}
\item alert count
\item suppression rate
\item usefulness precision
\item severity-tier precision
\item evidence-state breakdown
\item alert redundancy rate
\item worst holdout block
\end{itemize}

\textbf{Section 5: Lead-Time Scorecard}
\begin{itemize}
\item median lead time
\item interquartile lead time
\item short-lead alert share
\item near-resolution trigger share
\item lead time by severity tier
\item weakest lead-time block
\end{itemize}

\textbf{Section 6: Paper-Trade Scorecard}
\begin{itemize}
\item trade eligibility rate
\item fill rate
\item skip rate by reason
\item median bounded PnL
\item hit rate
\item loss rate
\item worst decile PnL
\item holding duration summary
\item weakest trade-performance block
\end{itemize}

\textbf{Section 7: Weak-Regime And Failure Review}
\begin{itemize}
\item weakest event-family block
\item weakest category block
\item weakest time block
\item top-category dependency share
\item top-event-family dependency share
\item dominant failure reason codes
\item whether positive performance disappears under stricter conservative assumptions
\end{itemize}

\textbf{Section 8: Interpretation Summary}
\begin{itemize}
\item strongest regime
\item weakest regime
\item whether performance is broad or narrow
\item whether lead time is operationally meaningful
\item whether simulated trade edge survives conservative assumptions
\item recommendation:
\texttt{promising},
\texttt{mixed},
or \texttt{not\_yet\_defendable}
\end{itemize}

\subsection*{Report Status Labels}

\begin{itemize}
\item \texttt{promising}: success metrics remain positive across multiple scored holdout regimes and failure metrics do not show dominant narrow-regime dependence.
\item \texttt{mixed}: some regimes look strong, but weak-regime or concentration signals prevent broad claims.
\item \texttt{not\_yet\_defendable}: performance relies on too few windows, too few categories, too much missing coverage, or collapses under conservative assumptions.
\end{itemize}

\section*{Aggregation And Headline Reporting Rules}

\begin{itemize}
\item No headline metric may be shown without its holdout-regime breakdown.
\item No pooled metric may combine event-family, category, and time-split results into one signoff score.
\item If a summary aggregate is shown, it must be labeled \texttt{descriptive\_only} unless all underlying scored blocks satisfy Task 2 minimum sample and coverage rules.
\item The report must always display:
best block,
median scored block,
and worst scored block
for each primary metric family.
\item Any claim of historical usefulness must cite both a success view and a failure view from the same reporting run.
\end{itemize}

\section*{Minimum Reporting Requirements}

\begin{itemize}
\item At least one metric from each family must appear in the top-level report:
candidate quality,
alert usefulness,
lead time,
paper-trade performance,
and failure metrics.
\item Every top-level report must include at least one weak-regime table.
\item Every top-level report must include one coverage summary table.
\item Every top-level report must identify one historical window suitable for a strongest-case study and one for a failure-case study.
\end{itemize}

\section*{Review Checklist}

\begin{itemize}
\item Does the metrics catalog define success and failure views for each unit?
\item Does the report template force holdout-regime segmentation instead of pooled-only reporting?
\item Are coverage-insufficient and descriptive-only splits still visible?
\item Are weak regimes and concentration risks shown alongside favorable results?
\item Can another engineer generate the same report from the same validation run inputs and versions?
\end{itemize}

\section*{Done Condition}

\begin{itemize}
\item One metrics catalog exists.
\item One reusable backtesting report template exists.
\item Reporting includes both success views and failure views for candidates, alerts, lead time, and simulated trades.
\end{itemize}

\end{document}
