\documentclass{article}
\usepackage[margin=1in]{geometry}
\begin{document}

\section*{Phase 1 Gate 1 Signoff - Person 2}

\textbf{Phase:} 1\\
\textbf{Owner:} Person 2 (Person B)\\
\textbf{Source of truth:} \texttt{Documentation/SRS.tex}, Section 11.4\\
\textbf{Related artifacts:}
\begin{itemize}
\item \texttt{Documentation/person2Phases/phase1\_validation\_contract.tex}
\item \texttt{config/phase1\_validation.yaml}
\item \texttt{Documentation/person2Phases/phase1\_qa\_sample\_review.csv}
\end{itemize}

\section*{Summary}

This document is the Gate 1 evidence pack and signoff template for Person 2
Phase 1 work. It should be completed after the automated validators and manual
QA sample review have been executed against the current approved market
universe.

\section*{Automated Validation Evidence}

\begin{itemize}
\item Validation run timestamp: \underline{\hspace{8cm}}
\item Config version: \underline{\hspace{8cm}}
\item Approved universe source/version: \underline{\hspace{8cm}}
\item Overall validation status: \underline{\hspace{8cm}}
\end{itemize}

\textbf{Checks}
\begin{itemize}
\item Both-side asset coverage: \underline{\hspace{4cm}}
\item Duplicate trade inflation: \underline{\hspace{4cm}}
\item Wallet-field null-rate: \underline{\hspace{4cm}}
\item Condition-id population: \underline{\hspace{4cm}}
\item \texttt{first\_seen\_at} semantics: \underline{\hspace{4cm}}
\item Fresh-wallet semantics: \underline{\hspace{4cm}}
\item Episode linkage semantics: \underline{\hspace{4cm}}
\end{itemize}

\section*{Manual QA Evidence}

\begin{itemize}
\item QA sample sheet path: \underline{\hspace{8cm}}
\item Episode sample count reviewed: \underline{\hspace{8cm}}
\item Reviewer: \underline{\hspace{8cm}}
\item Review completion date: \underline{\hspace{8cm}}
\end{itemize}

\textbf{QA Findings Summary}
\begin{itemize}
\item Passed episodes: \underline{\hspace{4cm}}
\item Failed episodes: \underline{\hspace{4cm}}
\item Common failure taxonomy: \underline{\hspace{8cm}}
\item Highest-severity issue found: \underline{\hspace{8cm}}
\end{itemize}

\section*{Handoffs To Person 1}

\begin{itemize}
\item Validation failures with concrete failing records and reason codes:
\underline{\hspace{8cm}}
\item Universe leakage or selector mismatches:
\underline{\hspace{8cm}}
\item Schema or parser corrections required:
\underline{\hspace{8cm}}
\item Duplicate inflation or wallet-null trends requiring action:
\underline{\hspace{8cm}}
\end{itemize}

\section*{Gate 1 Checklist}

\begin{itemize}
\item Canonical validation spec is complete and versioned. \underline{\hspace{2cm}}
\item Approved-universe behavior is validated or explicitly explained. \underline{\hspace{2cm}}
\item Automated validation suite produced reproducible outputs. \underline{\hspace{2cm}}
\item Deterministic semantic rules are documented and executed. \underline{\hspace{2cm}}
\item Manual review of at least 20 episodes is complete. \underline{\hspace{2cm}}
\item Findings have been handed off to Person 1 where needed. \underline{\hspace{2cm}}
\end{itemize}

\section*{Signoff}

\begin{itemize}
\item Person 2 signoff: \underline{\hspace{8cm}}
\item Shared Gate 1 signoff with Person 1: \underline{\hspace{8cm}}
\end{itemize}

\end{document}
