\documentclass{article}
\usepackage[margin=1in]{geometry}
\begin{document}
\section*{Documentation Index}

This index is meant to answer two questions quickly:
\begin{itemize}
\item what is the canonical source of truth,
\item which documents and artifact families are active versus legacy as the repo moves through Phase 8 closeout.
\end{itemize}

\begin{itemize}
\item \texttt{Documentation/SRS.tex}: v4.1 integrated SRS (source of truth).
\item \texttt{Documentation/phases/phase8\_canonical\_inventory.tex}: master canonical inventory for Phase 1 through Phase 7 committed artifacts.
\item \texttt{Documentation/phases/phase8.tex}: single-owner Phase 8 closeout and consolidation plan.
\item \texttt{Documentation/phases/phase8\_reference\_path.tex}: frozen end-to-end reference path and reproducibility gap record for Phase 8 Task 2.
\item \texttt{Documentation/phases/phase8\_v1\_operating\_mode.tex}: formal canonical v1 operating-mode decision for Phase 8 Task 3.
\item \texttt{Documentation/phases/phase8\_metrics\_review.tex}: final metrics bundle, limitations review, and stop-condition ledger for Phase 8 Task 4.
\item \texttt{Documentation/phases/phase8\_final\_closeout.tex}: final handoff package, consolidated runbook path, and SRS closeout memo for Phase 8 Task 5.
\item \texttt{Documentation/phases/phase9.tex}: single-owner Phase 9 evidence-materialization and SRS-completion plan derived from the remaining gaps recorded by Phase 8.
\item \texttt{Documentation/phases/phase9\_task1\_reference\_window.tex}: Phase 9 Task 1 selection, availability check, and frozen command/output contract for the canonical reference window.
\item \texttt{Documentation/phases/phase9\_task2\_candidate\_to\_alert.tex}: Phase 9 Task 2 candidate, evidence, alert, delivery, and analyst-workflow materialization record for the canonical reference hour.
\item \texttt{Documentation/phases/phase9\_task3\_replay\_validation.tex}: Phase 9 Task 3 replay, holdout-validation, and conservative paper-trading materialization record for the same canonical hour.
\item \texttt{Documentation/phases/phase9\_task4\_phase6\_model\_completion.tex}: Phase 9 Task 4 boosted-tree model, baseline-comparison, calibration, registry, and shadow-score materialization record.
\item \texttt{Documentation/phases/phase9\_task5\_closeout\_refresh.tex}: Phase 9 Task 5 single-owner runbook consolidation and refreshed Phase 8 closeout package contract.
\item \texttt{Documentation/phases/phase10.tex}: single-owner Phase 10 operational-hardening, real-provider validation, and final SRS-v1 completion plan derived from the remaining Phase 9 blockers.
\item \texttt{Documentation/phases/phase10\_task1\_real\_provider\_evidence.tex}: Phase 10 Task 1 real-provider-backed evidence hardening contract and canonical execution command.
\item \texttt{Documentation/phases/phase10\_task2\_analyst\_loop\_expansion.tex}: Phase 10 Task 2 repeated alert-episode, analyst-feedback, and suppression-review contract and canonical execution command.
\item \texttt{Documentation/phases/phase10\_task3\_heldout\_validation.tex}: Phase 10 Task 3 frozen held-out window family, replay-linked validation pack, and conservative backtest contract.
\item \texttt{Documentation/phases/phase10\_task4\_heldout\_model\_completion.tex}: Phase 10 Task 4 held-out LightGBM, baseline comparison, calibration, registry, and shadow-score contract.
\item \texttt{Documentation/phases/phase10\_task5\_ops\_governance\_closeout.tex}: Phase 10 Task 5 operations, security, governance, operating-mode, and final completion contract.
\item \texttt{Documentation/phases/phase2.tex}: canonical Phase 2 delivery summary and evidence.
\item \texttt{Documentation/phases/phase2\_gate2\_signoff.tex}: Gate 2 evidence pack and signoff memo.
\item \texttt{Documentation/phases/phase4.tex}: canonical Phase 4 single-owner alert and evidence workflow plan.
\item \texttt{Documentation/phases/phase4\_gate4\_signoff.tex}: Gate 4 signoff memo for the local alert loop.
\item \texttt{Documentation/phases/phase5.tex}: canonical Phase 5 replay, backtesting, and validation plan.
\item \texttt{Documentation/SRS\_audit.tex}: audit findings (companion).
\item \texttt{Documentation/polymarket\_research\_srs.tex}: research notes (companion).
\item \texttt{Documentation/reference\_repo\_analysis.tex}: repo/codebase analysis (companion).
\item \texttt{Documentation/phases/}: canonical single-owner phase plans.
\item \texttt{Documentation/references/}: raw reference exports used while drafting the SRS.
\item \texttt{Documentation/person1Phases/}: legacy split-by-person planning docs; some later-phase notes remain supporting references only.
\item \texttt{Documentation/person2Phases/}: legacy split-by-person planning docs and support artifacts; some later-phase notes remain supporting references only.
\end{itemize}

\textbf{Canonical path for startup and handoff:}
\texttt{README.md} $\rightarrow$ \texttt{Documentation/INDEX.tex} $\rightarrow$
\texttt{Documentation/SRS.tex} $\rightarrow$
\texttt{Documentation/phases/phase8\_canonical\_inventory.tex} $\rightarrow$
\texttt{Documentation/phases/phase8\_final\_closeout.tex} $\rightarrow$
\texttt{Documentation/phases/phase9.tex} $\rightarrow$
\texttt{Documentation/phases/phase10.tex}

\textbf{Canonical note:} \texttt{Documentation/phases/} is the single-owner
planning and closeout folder.\\
\textbf{Authority note:} when both \texttt{.tex} and \texttt{.pdf} versions
exist, the \texttt{.tex} source is authoritative.\\
\textbf{Legacy note:} the split-by-person folders are retained mainly for
historical reference; they should only be used when this index or the Phase 8
inventory explicitly classifies a later-phase artifact as supporting active.

\end{document}
