% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\documentclass[
]{article}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{longtable,booktabs,array}
\newcounter{none} % for unnumbered tables
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\section{Software Requirements
Specification}\label{software-requirements-specification}

\subsection{Polymarket Insider-Signal Detection and Leading Indicator
Engine}\label{polymarket-insider-signal-detection-and-leading-indicator-engine}

\textbf{Version:} 4.1\\
\textbf{Date:} April 18, 2026\\
\textbf{Owner:} Vraj Patel\\
\textbf{Status:} Final integrated source of truth\\
\textbf{Implementation readiness:} Not Ready until Stage Gate 2,
Section 2.5, and the exit criteria for Phase 0 and Phase 1 are
passed\\
\textbf{Canonical document:} \texttt{Documentation/SRS.tex}\\
\textbf{Companion documents:} \texttt{Documentation/SRS\_audit.tex},
\texttt{Documentation/reference\_repo\_analysis.tex},
\texttt{Documentation/polymarket\_research\_srs.tex}

\begin{quote}
This v4 document supersedes v3 and integrates the audit findings as
binding requirements. If any supporting document disagrees with this
file, the stricter requirement in this file wins.
\end{quote}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{Table of Contents}\label{table-of-contents}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \hyperref[1-mission-scope-and-current-truth]{Mission, Scope, and
  Current Truth}
\item
  \hyperref[2-research-hypotheses-and-product-success]{Research
  Hypotheses and Product Success}
\item
  \hyperref[3-canonical-architecture]{Canonical Architecture}
\item
  \hyperref[4-data-contracts-and-semantics]{Data Contracts and
  Semantics}
\item
  \hyperref[5-concrete-remediation-program]{Concrete Remediation
  Program}
\item
  \hyperref[6-detection-and-ml-strategy]{Detection and ML Strategy}
\item
  \hyperref[7-evidence-alerting-and-analyst-workflow]{Evidence,
  Alerting, and Analyst Workflow}
\item
  \hyperref[8-replay-backtesting-and-validation]{Replay, Backtesting,
  and Validation}
\item
  \hyperref[9-operations-security-and-governance]{Operations, Security,
  and Governance}
\item
  \hyperref[10-cost-model-and-budget]{Cost Model and Budget}
\item
  \hyperref[11-roadmap-and-stage-gates]{Roadmap and Stage Gates}
\item
  \hyperref[12-external-sources]{External Sources}
\end{enumerate}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{1. Mission, Scope, and Current
Truth}\label{1-mission-scope-and-current-truth}

\subsubsection{1.1 Mission}\label{11-mission}

Build a wallet-aware market-intelligence system for Polymarket that:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Detects abnormal market episodes in near real time.
\item
  Scores whether the episode looks more informed than noisy.
\item
  Tests whether the episode leads public information discovery or future
  repricing.
\item
  Delivers replayable, explainable alerts.
\end{enumerate}

This system is a research and monitoring platform first. It is not an
accusation engine, not a social surveillance product, and not an
automated trading bot by default.

\subsubsection{1.2 In Scope}\label{12-in-scope}

\begin{itemize}
\tightlist
\item
  Polymarket public market-data ingestion across Gamma, CLOB/Data API,
  and WebSocket feeds.
\item
  Wallet-aware event detection using public identifiers such as
  \texttt{proxyWallet}.
\item
  External evidence retrieval after a candidate episode is detected.
\item
  Human-facing alerting, replay, backtesting, and research validation.
\item
  Conservative paper-trading evaluation.
\end{itemize}

\subsubsection{1.3 Explicit Non-Goals}\label{13-explicit-non-goals}

\begin{itemize}
\tightlist
\item
  Identifying real-world persons behind wallets.
\item
  Claiming illegal insider trading.
\item
  Building a high-frequency execution engine in v1.
\item
  Training deep models before the data contract is stable.
\item
  Treating external search silence as truth without retrieval
  benchmarking.
\end{itemize}

\subsubsection{1.4 Current Repo Truth}\label{14-current-repo-truth}

The current repository is a good collector foundation and not yet a
production-ready detection platform.

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}lll@{}}
\toprule\noalign{}
Area & Current Truth & Consequence \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Market universe & Sports-only filter is active in the collector & H2/H3
cannot be tested across the actual target universe \\
Trade ingestion & Trade pull path is still not aligned with the
condition-level semantics required by the SRS & Wallet-aware episode
construction is unreliable \\
Asset coverage & Live path is still biased toward YES-side coverage &
Order-flow state is incomplete \\
Trade schema & No \texttt{proxy\_wallet}, \texttt{transaction\_hash},
\texttt{condition\_id}, \texttt{outcome\_side}, or wallet profile fields
in the canonical trade table & Core entity model does not exist yet \\
Retention & Closed-market microstructure is still deleted after 24 hours
& Event studies and label generation are corrupted \\
Storage & Local SQLite database is already very large & Canonical local
execution must graduate to raw archives plus local PostgreSQL, not stay
SQLite-only \\
ML & \texttt{ml\_pipeline/feature\_builder.py} is still a stub & No
trustworthy model training path exists \\
\end{longtable}
}

\subsubsection{1.5 Hard Truth}\label{15-hard-truth}

The project is currently in the \textbf{data-correctness and
state-contract phase}, not the \textbf{modeling and alert-ranking
phase}.

The main problem to solve is not model sophistication. The main problem
is building a replayable, semantically correct, wallet-aware event
pipeline.

\subsubsection{1.6 What v4 Changes}\label{16-what-v4-changes}

Version 4 turns the earlier SRS plus audit into one implementation
contract. The project is no longer defined as a broad research ambition.
It is now defined as a staged delivery program with audit-derived hard
requirements.

\begin{itemize}
\tightlist
\item
  Audit findings are converted into requirements, not left as side
  commentary.
\item
  Any requirement that protects replayability, data correctness, or
  operational cost takes precedence over optional modeling ambition.
\item
  v1 scope is explicitly constrained to a reliable collector, replayable
  data plane, deterministic detector, evidence-backed alert loop, and
  one defendable baseline model family.
\item
  Deep models, graph neural networks, and execution automation remain
  out of v1 unless all readiness gates are already passed.
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{2. Research Hypotheses and Product
Success}\label{2-research-hypotheses-and-product-success}

\subsubsection{2.1 Primary Research
Hypotheses}\label{21-primary-research-hypotheses}

\paragraph{H1: Observability / Goodhart
Hypothesis}\label{h1-observability--goodhart-hypothesis}

Signals that are operationally useful may lose tradable edge as they
become more widely observed, even if calibration improves.

\paragraph{H2: Fresh-Wallet Flow
Hypothesis}\label{h2-fresh-wallet-flow-hypothesis}

Coordinated flow from previously unseen or low-footprint wallets
contains incremental predictive information beyond wallet-unaware
microstructure features.

\paragraph{H3: Leading Indicator
Hypothesis}\label{h3-leading-indicator-hypothesis}

Wallet-aware flow episodes can lead either:

\begin{itemize}
\tightlist
\item
  future Polymarket repricing,
\item
  cross-market repricing, or
\item
  public information arrival.
\end{itemize}

\subsubsection{2.2 Product Success
Conditions}\label{22-product-success-conditions}

The system is successful only if all of the following are true:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Raw event ingestion is durable and replayable.
\item
  Episode reconstruction is deterministic from raw archives.
\item
  Wallet-aware features beat wallet-unaware baselines on ranking
  quality.
\item
  Top-ranked alerts produce measurable lead time or economic edge after
  conservative slippage assumptions.
\item
  Alert volume and false-positive rate remain operationally usable.
\end{enumerate}

\subsubsection{2.3 Terminology Rules}\label{23-terminology-rules}

\begin{itemize}
\tightlist
\item
  \textbf{Previously unseen wallet} means unseen in our point-in-time
  archive, not new to the world.
\item
  \textbf{Wallet cluster} means a statistical grouping used for
  modeling, not a verified identity.
\item
  \textbf{Potential informed flow} is acceptable language.
\item
  \textbf{Insider} is not acceptable language in user-facing outputs.
\end{itemize}

\subsubsection{2.4 Audit-Integrated Non-Negotiables}\label{24-audit-integrated-non-negotiables}

The following rules are mandatory and come directly from the audit:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The system must be designed as separate sensing, state, decision,
  evidence, and research planes. It must not be treated as one undivided
  stack.
\item
  A durable raw event log is mandatory before serious detector or model
  claims are made.
\item
  Wallets and wallet clusters are modeling entities, not verified human
  identities.
\item
  ``First seen'' claims must carry provenance and confidence, not just a
  timestamp.
\item
  External evidence retrieval must be asynchronous, cached, and
  benchmarked before ``public silence'' is treated as a useful feature.
\item
  Label definitions, analyst feedback, and conservative execution logic
  must exist before supervised ranking results are treated as credible.
\item
  v1 must use deterministic rules plus tabular ranking before any
  advanced deep sequence or graph model is attempted.
\item
  Runtime and vendor decisions must be justified with real cost and
  operational constraints, not convenience assumptions.
\end{enumerate}

\subsubsection{2.5 Implementation Readiness Checklist}\label{25-implementation-readiness-checklist}

This project is not implementation-ready in the full-system sense until
all checklist items below are true.

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}lll@{}}
\toprule\noalign{}
Requirement & Why It Exists & Ready When \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Durable raw archive & Prevents non-replayable data loss & All inbound
payloads are archived immutably before normalization \\
Event-time contract & Prevents replay corruption & Event time, ingest
time, watermarking, and late-event rules are implemented \\
Wallet-linked ingestion & Prevents fake signal logic & Trade rows include
wallet and condition identifiers with validated coverage \\
Label specification & Prevents misleading model evaluation & Horizons,
censoring, exclusions, and operational labels are defined in writing \\
Cost realism & Prevents architecture drift and budget shock & Runtime,
storage, queueing, and evidence-provider budgets are numerically
credible \\
End-to-end replay proof & Prevents false confidence & One historical
window can be replayed from raw data to final alert deterministically \\
\end{longtable}
}

\subsubsection{2.6 Definition of v1 Complete}\label{26-definition-of-v1-complete}

Version 1 of this project is complete when all of the following are
true:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  the collector runs stably across the intended market universe,
\item
  the raw archive and replay path are working,
\item
  deterministic candidate episodes can be regenerated from replay,
\item
  evidence-backed alerts are live with analyst feedback capture,
\item
  one conservative backtest and one paper-trading evaluation exist, and
\item
  one LightGBM or CatBoost ranker is evaluated against the wallet-unaware
  baselines.
\end{enumerate}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{3. Canonical Architecture}\label{3-canonical-architecture}

\subsubsection{3.1 Architecture
Principles}\label{31-architecture-principles}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Separate sensing, state, decision, evidence, and research into
  distinct planes.
\item
  Make raw data immutable before normalization.
\item
  Treat replayability as a first-class requirement, not a future
  improvement.
\item
  Keep external evidence retrieval off the sub-second hot path.
\item
  Keep v1 models CPU-cheap, interpretable, and reproducible.
\end{enumerate}

\subsubsection{3.2 Canonical Deployment
Topology}\label{32-canonical-deployment-topology}

The final source-of-truth deployment for v1 is a local-first
architecture. The whole system runs on one workstation or small server,
while still connecting to external APIs for live market data and
evidence retrieval.

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}llll@{}}
\toprule\noalign{}
Plane & Service & Runtime & Purpose \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Sensing & \texttt{collector-stream} & Long-lived local process &
WebSocket listener and REST pollers \\
Durable log & \texttt{raw-event-log} & Local append-only filesystem
archive & Immutable payload archive plus replay source of truth \\
Operational store & \texttt{market-intel-db} & Local PostgreSQL &
Relational state, alert history, analyst feedback \\
Online state & \texttt{signal-state} & Local Redis service & Rolling
windows, suppression windows, hot keyed state \\
Decision & \texttt{detector} & Local Python worker & Candidate
generation and episode scoring \\
Evidence & \texttt{evidence-worker} & Local async worker & X/web/news
enrichment after a candidate exists \\
Alerting & \texttt{alert-worker} & Local Python worker &
Telegram/Discord/Twilio integration \\
Research & \texttt{replay-backtest} & Local batch jobs & Point-in-time
rebuilds, validation, retraining \\
Ops & Local logs + OS service manager + backups & Local platform
services & Metrics, logging, secrets, restart policy, backups \\
\end{longtable}
}

\subsubsection{3.3 Why v1 Runs Locally
First}\label{33-why-v1-runs-locally-first}

Local-first execution is the canonical v1 path because:

\begin{itemize}
\tightlist
\item
  the collector is long-lived and stateful,
\item
  local raw archives and replay artifacts are easier to inspect,
  reproduce, and back up for a thesis workflow,
\item
  avoiding cross-service hops makes debugging ingestion, replay, and
  feature drift substantially easier for a two-person team,
\item
  the first learned model family is CPU-cheap and does not require
  distributed infrastructure.
\end{itemize}

Cloud deployment remains optional later, but it is not the source of
truth for v1.

\subsubsection{3.4 End-to-End Data Flow}\label{34-end-to-end-data-flow}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Collector receives WebSocket and REST payloads.
\item
  Every payload is wrapped in a raw event envelope.
\item
  Raw envelopes are written to local append-only partitions.
\item
  Normalized lightweight envelopes are persisted into a local detector
  input log.
\item
  Detector consumes the local input log and updates local Redis rolling
  state.
\item
  Candidate rules and streaming anomaly features emit
  \texttt{signal\_candidates}.
\item
  Episode ranker scores only candidate episodes.
\item
  Evidence worker enriches the candidate asynchronously.
\item
  Alert worker applies suppression, severity, and delivery policy.
\item
  All alerts, analyst actions, model versions, and evidence snapshots
  are stored in local PostgreSQL.
\item
  Replay jobs rebuild features and labels from raw archives, not from
  mutable live tables alone.
\end{enumerate}

\subsubsection{3.5 Canonical Service
Boundaries}\label{35-canonical-service-boundaries}

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}lll@{}}
\toprule\noalign{}
Service & Must Do & Must Not Do \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Collector & Write immutable raw events and normalized envelopes &
Compute final alerts \\
Detector & Build rolling state and score episodes & Fetch slow external
evidence on the hot path \\
Evidence worker & Fetch and cache external evidence snapshots & Decide
whether raw market anomaly exists \\
Alert worker & Render, suppress, route, and log alerts & Change
historical scores retroactively \\
Replay jobs & Rebuild historical state from raw archives & Read mutable
live tables as the sole source of truth \\
\end{longtable}
}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{4. Data Contracts and
Semantics}\label{4-data-contracts-and-semantics}

\subsubsection{4.1 Raw Event Envelope}\label{41-raw-event-envelope}

Every inbound payload must be persisted as a raw event envelope before
normalization.

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}lll@{}}
\toprule\noalign{}
Field & Type & Description \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
\texttt{event\_uuid} & UUID & Internal immutable id for this captured
payload \\
\texttt{source\_system} & string & \texttt{gamma}, \texttt{clob\_rest},
\texttt{ws\_market}, \texttt{activity\_api}, \texttt{positions\_api},
\texttt{profile\_api}, etc. \\
\texttt{source\_endpoint} & string & Concrete endpoint or channel
name \\
\texttt{schema\_version} & string & Version of the raw envelope
contract \\
\texttt{source\_event\_id} & string nullable & Provider id if
available \\
\texttt{event\_time} & timestamp nullable & Provider event timestamp if
available \\
\texttt{ingest\_time} & timestamp & Time received by our collector \\
\texttt{market\_id} & string nullable & Internal normalized market id if
known \\
\texttt{condition\_id} & string nullable & Condition identifier if
known \\
\texttt{asset\_id} & string nullable & Token/asset id if known \\
\texttt{wallet\_id} & string nullable & Raw wallet/proxy wallet if
present \\
\texttt{payload\_json} & json & Unmodified provider payload \\
\texttt{payload\_hash} & string & Content hash used for dedupe and
integrity checks \\
\texttt{collector\_version} & string & Git SHA or release tag of the
collector \\
\end{longtable}
}

\subsubsection{4.2 Canonical Normalized
Tables}\label{42-canonical-normalized-tables}

The normalized relational schema must include at minimum:

\begin{itemize}
\tightlist
\item
  \texttt{events}
\item
  \texttt{markets}
\item
  \texttt{market\_snapshots}
\item
  \texttt{order\_book\_snapshots}
\item
  \texttt{trades\_raw}
\item
  \texttt{wallets}
\item
  \texttt{wallet\_profiles}
\item
  \texttt{wallet\_first\_seen}
\item
  \texttt{wallet\_activity}
\item
  \texttt{wallet\_positions}
\item
  \texttt{wallet\_cluster\_membership}
\item
  \texttt{signal\_candidates}
\item
  \texttt{signal\_episodes}
\item
  \texttt{signal\_features}
\item
  \texttt{signal\_scores}
\item
  \texttt{external\_evidence}
\item
  \texttt{alerts}
\item
  \texttt{alert\_delivery}
\item
  \texttt{alert\_feedback}
\item
  \texttt{model\_registry}
\item
  \texttt{replay\_runs}
\item
  \texttt{data\_quality\_metrics}
\end{itemize}

\subsubsection{4.3 Time Semantics}\label{43-time-semantics}

The old SRS did not define time correctly. This document does.

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}lll@{}}
\toprule\noalign{}
Term & Definition & Required Use \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
\texttt{event\_time} & Provider timestamp when the event actually
occurred & Used for replay and historical feature windows \\
\texttt{ingest\_time} & Timestamp when the collector received the event
& Used for lag monitoring and outage detection \\
\texttt{processing\_time} & Timestamp when downstream worker handled the
event & Used for pipeline SLOs \\
\texttt{watermark\_time} & Latest event-time boundary considered stable
for a window & Used to handle out-of-order events \\
\end{longtable}
}

Rules:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Feature windows must be based on \texttt{event\_time}, not
  \texttt{ingest\_time}.
\item
  Lag metrics must compare \texttt{ingest\_time} against
  \texttt{event\_time}.
\item
  Replays must respect event ordering plus late-arrival handling rules.
\item
  Backtests must never use profile data or evidence snapshots that were
  unavailable at decision time.
\end{enumerate}

\subsubsection{4.4 Dedupe and Source
Priority}\label{44-dedupe-and-source-priority}

The system must dedupe across WebSocket, REST polling, and backfill
sources.

Canonical rules:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Prefer provider-native ids when present.
\item
  If no provider-native id exists, use a deterministic surrogate key
  composed from source, asset, event time, side, price, and size.
\item
  Mark the highest-fidelity source as canonical for overlapping
  observations.
\item
  Never count the same economic trade twice because it arrived through
  both WebSocket and REST backfill.
\end{enumerate}

\subsubsection{4.5 Entity Semantics}\label{45-entity-semantics}

\paragraph{Wallet}\label{wallet}

A wallet entity is a public on-platform identifier such as
\texttt{proxyWallet}. It is not a human identity.

\paragraph{First Seen}\label{first-seen}

\texttt{first\_seen\_at} means the earliest timestamp observed in our
immutable archive, not the earliest time the wallet existed on the
platform.

\paragraph{Wallet Cluster}\label{wallet-cluster}

A wallet cluster is a model-generated grouping based on repeated
co-participation, timing, directionality, and event-family overlap.
Clusters are versioned. Cluster membership can change over time.

\paragraph{Fresh Wallet}\label{fresh-wallet}

A fresh-wallet flag is computed, not absolute. It must be backed by:

\begin{itemize}
\tightlist
\item
  first-seen timestamp in our archive,
\item
  total known trading footprint,
\item
  profile age if available,
\item
  confidence flag indicating whether downtime or backfill gaps could
  invalidate the claim.
\end{itemize}

\subsubsection{4.6 Retention Policy}\label{46-retention-policy}

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}llll@{}}
\toprule\noalign{}
Data Type & Hot Retention & Cold Retention & Notes \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Raw event envelopes & 30-90 days & 1+ year & Immutable on local disk
with checksum and backup \\
Normalized trades/activity & 1+ year & 1+ year & No destructive TTL
before archival \\
Feature tables & 180+ days & Rebuildable & Versioned by feature
schema \\
Alerts and analyst feedback & Permanent & Permanent & Needed for model
evaluation \\
Evidence snapshots & 180+ days & 1+ year & Must preserve timestamps and
query metadata \\
\end{longtable}
}

The 24-hour destructive TTL on closed-market microstructure is not
allowed in the canonical design.

\subsubsection{4.7 Assumption-to-Requirement
Conversion}\label{47-assumption-to-requirement-conversion}

The audit identified several assumptions that were too vague to build
from safely. In v4, those assumptions are converted into direct
requirements.

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}p{5.2cm}p{9.0cm}@{}}
\toprule\noalign{}
Requirement & Audit issue resolved \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Only model observable public-feed features unless a proxy estimator is
explicitly defined & Prevents pretending the public feed exposes full
order lifecycle information \\
Never equate wallet identity with human identity & Prevents false
attribution and legal/ethical overreach \\
Attach provenance to \texttt{first\_seen} and fresh-wallet flags &
Prevents collector gaps from creating fake novelty \\
Budget and prioritize enrichment calls & Prevents API fan-out from
destroying latency and quotas \\
Treat event time, ingest time, and watermarking as first-class metadata
& Prevents out-of-order episode corruption \\
Benchmark evidence retrieval before using ``public silence'' as a signal
& Prevents missing search results from being misread as market edge \\
Keep PostgreSQL as an operational store, not as the only replay log &
Prevents non-reproducible backtests and silent data holes \\
Define labels and simulator assumptions before model comparison & Prevents
misleading accuracy or PnL claims \\
Delay deep sequence and graph models until the feature contract is
stable & Prevents expensive overfitting on semantically weak data \\
Treat access control, auditability, and retention as product
requirements & Prevents governance from being postponed until too late \\
\end{longtable}
}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{5. Concrete Remediation
Program}\label{5-concrete-remediation-program}

This section converts the audit into concrete engineering work. No model
work proceeds until Work Package 0 and Work Package 1 are complete.

\subsubsection{5.1 Work Package 0: Stop Data Loss and Silent
Failure}\label{51-work-package-0-stop-data-loss-and-silent-failure}

\textbf{Objective:} Stop destroying data and start measuring pipeline
health.

\textbf{Tasks}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Disable destructive TTL deletion for closed-market trades, snapshots,
  and order books until raw archival is live.
\item
  Add collector heartbeat metrics: last WS event time, last REST success
  time, last full sync time, queue lag, and write failures.
\item
  Add source-level ingestion counters by minute.
\item
  Add restart-safe collector shutdown handling and restart
  observability.
\item
  Verify continuous collection for 72 hours without unexplained gaps.
\end{enumerate}

\textbf{Exit criteria}

\begin{itemize}
\tightlist
\item
  No research-critical data is deleted before archival.
\item
  Heartbeat and lag metrics exist and are queryable.
\item
  72-hour soak run completes without silent collector death.
\end{itemize}

\subsubsection{5.2 Work Package 1: Fix Ingestion
Correctness}\label{52-work-package-1-fix-ingestion-correctness}

\textbf{Objective:} Make the live dataset semantically usable.

\textbf{Tasks}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Remove the hard-coded sports filter and replace it with a configurable
  universe selector.
\item
  Subscribe to both YES and NO assets for live market coverage.
\item
  Correct the trade ingestion path so condition-level identifiers are
  captured correctly.
\item
  Expand the canonical trade schema to include:

  \begin{itemize}
  \tightlist
  \item
    \texttt{proxy\_wallet}
  \item
    \texttt{transaction\_hash}
  \item
    \texttt{condition\_id}
  \item
    \texttt{asset\_id}
  \item
    \texttt{outcome\_side}
  \item
    \texttt{price}
  \item
    \texttt{size}
  \item
    \texttt{usdc\_notional}
  \item
    \texttt{trade\_time}
  \item
    \texttt{source}
  \end{itemize}
\item
  Add wallet profile and traded-footprint enrichment hooks, but only
  after base trade capture is correct.
\item
  Add source-priority and dedupe logic between WS, REST, and backfill.
\end{enumerate}

\textbf{Exit criteria}

\begin{itemize}
\tightlist
\item
  Trades are captured with wallet-linked fields.
\item
  Both-side market activity is observable.
\item
  Duplicate trade inflation is measured and controlled.
\end{itemize}

\subsubsection{5.3 Work Package 2: Add a Durable Raw Event
Log}\label{53-work-package-2-add-a-durable-raw-event-log}

\textbf{Objective:} Make the pipeline replayable.

\textbf{Tasks}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Wrap every inbound payload in the raw event envelope defined in
  Section 4.1.
\item
  Write raw events to local disk as append-only compressed NDJSON or
  Parquet
  partitions:

  \begin{itemize}
  \tightlist
  \item
    \texttt{data/raw/year=YYYY/month=MM/day=DD/hour=HH/source\_system=...}
  \end{itemize}
\item
  Persist lightweight normalized envelopes into a local detector input
  log for downstream consumers.
\item
  Write archive manifest records into PostgreSQL with file path, time
  range, row count, checksum, and schema version.
\item
  Add a replay tool that can republish a chosen historical partition
  into the detector pipeline.
\end{enumerate}

\textbf{Exit criteria}

\begin{itemize}
\tightlist
\item
  Any 1-hour window can be replayed end to end from raw archives.
\item
  Raw archive integrity is verifiable by checksum and manifest.
\end{itemize}

\subsubsection{5.4 Work Package 3: Migrate to the Canonical Data
Plane}\label{54-work-package-3-migrate-to-the-canonical-data-plane}

\textbf{Objective:} Stop treating SQLite as the long-term operational
backbone while keeping the canonical runtime local.

\textbf{Tasks}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Stand up local PostgreSQL as the operational relational store.
\item
  Port the schema from SQLite to PostgreSQL with partitions for
  high-volume tables.
\item
  Keep local SQLite only as a dev cache or export target, not as
  canonical state.
\item
  Create PostgreSQL partitions for:

  \begin{itemize}
  \tightlist
  \item
    \texttt{market\_snapshots}
  \item
    \texttt{order\_book\_snapshots}
  \item
    \texttt{trades\_raw}
  \item
    \texttt{wallet\_activity}
  \end{itemize}
\item
  Add schema migration tooling and schema version table.
\end{enumerate}

\textbf{Exit criteria}

\begin{itemize}
\tightlist
\item
  New production writes land in PostgreSQL.
\item
  Partitions and indexes support the expected query patterns.
\item
  SQLite is no longer the authoritative operational store.
\end{itemize}

\subsubsection{5.5 Work Package 4: Build the Online State
Plane}\label{55-work-package-4-build-the-online-state-plane}

\textbf{Objective:} Make streaming episode detection operationally
possible.

\textbf{Tasks}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Introduce local Redis for rolling keyed state:

  \begin{itemize}
  \tightlist
  \item
    market rolling windows,
  \item
    wallet rolling windows,
  \item
    event-family windows,
  \item
    suppression windows.
  \end{itemize}
\item
  Define canonical rolling windows: 1m, 5m, 15m, 1h, 6h, 24h.
\item
  Store state needed for:

  \begin{itemize}
  \tightlist
  \item
    fresh-wallet counts,
  \item
    fresh-wallet notional,
  \item
    directional imbalance,
  \item
    concentration ratio,
  \item
    cross-market participation,
  \item
    volume acceleration,
  \item
    probability velocity and acceleration.
  \end{itemize}
\item
  Add late-event handling with watermark rules.
\item
  Add state reconciliation job that replays recent history and compares
  local Redis state against rebuilt state.
\end{enumerate}

\textbf{Exit criteria}

\begin{itemize}
\tightlist
\item
  Local Redis-backed streaming features match replayed historical
  features
  within tolerance.
\item
  Detector state survives normal restarts without corrupting episodes.
\end{itemize}

\subsubsection{5.6 Work Package 5: Build Deterministic Candidate
Detection}\label{56-work-package-5-build-deterministic-candidate-detection}

\textbf{Objective:} Emit candidate episodes before any expensive
enrichment.

\textbf{Tasks}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Implement deterministic episode rules using rolling features.
\item
  Add robust streaming statistics:

  \begin{itemize}
  \tightlist
  \item
    rolling median/MAD,
  \item
    exponentially weighted z-scores,
  \item
    change-point signals,
  \item
    tail-event thresholds.
  \end{itemize}
\item
  Persist each candidate with:

  \begin{itemize}
  \tightlist
  \item
    feature snapshot,
  \item
    feature-schema version,
  \item
    detector version,
  \item
    triggering rules,
  \item
    event-time window.
  \end{itemize}
\item
  Add cooldown and dedupe rules so one market burst does not spam
  multiple candidates.
\end{enumerate}

\textbf{Exit criteria}

\begin{itemize}
\tightlist
\item
  Candidate generation is reproducible from replay.
\item
  Candidate rate is operationally bounded and explainable.
\end{itemize}

\subsubsection{5.7 Work Package 6: Build the Evidence Layer
Properly}\label{57-work-package-6-build-the-evidence-layer-properly}

\textbf{Objective:} Prevent "public silence" from meaning "our search
stack failed."

\textbf{Tasks}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Build a provider abstraction for X and web/news search.
\item
  Store every evidence query, provider, timestamp, result count,
  latency, and raw response metadata.
\item
  Cache evidence snapshots point-in-time so future replays can
  reconstruct what was knowable.
\item
  Add retrieval evaluation using hand-labeled event cases.
\item
  Define an evidence timeout policy:

  \begin{itemize}
  \tightlist
  \item
    initial alert may ship without evidence,
  \item
    evidence update may follow asynchronously.
  \end{itemize}
\end{enumerate}

\textbf{Exit criteria}

\begin{itemize}
\tightlist
\item
  Retrieval quality is benchmarked on known historical events.
\item
  Evidence snapshots are replayable and timestamped.
\end{itemize}

\subsubsection{5.8 Work Package 7: Build Alerting and Analyst
Feedback}\label{58-work-package-7-build-alerting-and-analyst-feedback}

\textbf{Objective:} Turn detection into a usable analyst workflow.

\textbf{Tasks}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Define alert severities: \texttt{INFO}, \texttt{WATCH},
  \texttt{ACTIONABLE}, \texttt{CRITICAL}.
\item
  Send primary alerts to Telegram and archive/debug alerts to Discord.
\item
  Log every delivery attempt and delivery outcome.
\item
  Add analyst actions:

  \begin{itemize}
  \tightlist
  \item
    acknowledge,
  \item
    snooze,
  \item
    dismiss,
  \item
    mark as valuable,
  \item
    mark as false positive.
  \end{itemize}
\item
  Record suppression windows so the same event family does not page
  repeatedly without new evidence.
\end{enumerate}

\textbf{Exit criteria}

\begin{itemize}
\tightlist
\item
  Alerts are replayable.
\item
  Analyst actions are stored and usable as operational labels.
\end{itemize}

\subsubsection{5.9 Work Package 8: Build Replay and Backtesting Before
Fancy
ML}\label{59-work-package-8-build-replay-and-backtesting-before-fancy-ml}

\textbf{Objective:} Make historical validation trustworthy.

\textbf{Tasks}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Rebuild historical features from raw archives only.
\item
  Version feature definitions and detector thresholds.
\item
  Implement event-family holdout, category holdout, and time-split
  evaluation.
\item
  Build conservative paper-trading logic with fees, slippage, size caps,
  and near-resolution restrictions.
\item
  Add a one-command replay for known historical incidents.
\end{enumerate}

\textbf{Exit criteria}

\begin{itemize}
\tightlist
\item
  Any historical alert can be reproduced from raw data to final payload.
\item
  Backtest reports state exact model version, feature version, and
  archive range used.
\end{itemize}

\subsubsection{5.10 Work Package 9: Train the First Real
Model}\label{510-work-package-9-train-the-first-real-model}

\textbf{Objective:} Add learning only after the data plane is
trustworthy.

\textbf{Tasks}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Build episode-level training rows from candidate episodes.
\item
  Train a LightGBM or CatBoost ranker on engineered episode features.
\item
  Calibrate outputs by liquidity bucket and market family.
\item
  Compare against required wallet-unaware baselines.
\item
  Store model artifacts in a model registry with training dataset hash
  and feature schema version.
\end{enumerate}

\textbf{Exit criteria}

\begin{itemize}
\tightlist
\item
  Model beats wallet-unaware baselines on ranked alert quality.
\item
  Model outputs are calibrated enough for operational use.
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{6. Detection and ML
Strategy}\label{6-detection-and-ml-strategy}

\subsubsection{6.1 Modeling Order of
Operations}\label{61-modeling-order-of-operations}

The canonical modeling sequence is:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Deterministic candidate rules.
\item
  Streaming anomaly features over rolling windows.
\item
  Episode-level tabular ranker.
\item
  Graph-derived features and community detection.
\item
  Marked Hawkes or TCN sequence modeling after the data contract is
  stable.
\end{enumerate}

Deep transformers and graph neural networks are explicitly deferred.

\subsubsection{6.2 Required Feature
Families}\label{62-required-feature-families}

\paragraph{Market Microstructure}\label{market-microstructure}

\begin{itemize}
\tightlist
\item
  probability change
\item
  probability velocity
\item
  probability acceleration
\item
  bid-ask spread
\item
  depth imbalance
\item
  order-book resiliency
\item
  realized volatility
\item
  large-trade share
\item
  aggressive flow imbalance
\end{itemize}

\paragraph{Wallet / Cluster}\label{wallet--cluster}

\begin{itemize}
\tightlist
\item
  first-seen age
\item
  profile age if available
\item
  traded-footprint count
\item
  first-trade notional
\item
  fresh-wallet count by window
\item
  fresh-wallet notional share
\item
  concentration ratio
\item
  repeated same-direction participation
\item
  event-family overlap
\item
  cluster persistence
\end{itemize}

\paragraph{Context}\label{context}

\begin{itemize}
\tightlist
\item
  category
\item
  time to resolution
\item
  event popularity
\item
  event-family breadth
\item
  cross-market linkage strength
\item
  market liquidity bucket
\end{itemize}

\paragraph{Evidence}\label{evidence}

\begin{itemize}
\tightlist
\item
  X hit count
\item
  reranked top-post score
\item
  web/news hit count
\item
  corroboration lag
\item
  contradiction score
\item
  evidence freshness
\end{itemize}

\subsubsection{6.3 Canonical Labels}\label{63-canonical-labels}

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}lll@{}}
\toprule\noalign{}
Label Class & Label & Definition \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Market & \texttt{ret\_5m}, \texttt{ret\_30m}, \texttt{ret\_2h},
\texttt{ret\_24h} & Forward probability move after episode time \\
Research & \texttt{time\_to\_public\_corroboration} & Minutes until
first trusted public corroboration \\
Research & \texttt{time\_to\_cross\_market\_move} & Minutes until linked
market reprices materially \\
Operational & \texttt{alert\_value} & Analyst judged useful vs not
useful \\
Operational & \texttt{alert\_precision\_class} & true positive / false
positive / ambiguous \\
Economic & \texttt{paper\_trade\_pnl} & PnL under conservative execution
assumptions \\
\end{longtable}
}

\subsubsection{6.4 Required Baselines}\label{64-required-baselines}

The wallet-aware system must beat:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  raw probability momentum only,
\item
  order imbalance only,
\item
  wallet-unaware microstructure ranker,
\item
  external evidence only,
\item
  simple fresh-wallet threshold heuristic.
\end{enumerate}

\subsubsection{6.5 Model Choices}\label{65-model-choices}

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}ll@{}}
\toprule\noalign{}
Need & Canonical Model \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Candidate generation & deterministic rules + robust rolling
statistics \\
First learned ranker & LightGBM or CatBoost \\
Rare behavior support & EVT tail features and robust z-scores before
one-class methods \\
Temporal dynamics & marked Hawkes first, TCN second \\
Graph structure & community detection + graph-derived features before
any GNN \\
Explanations & small LLM only for alert summarization, never for core
scoring \\
\end{longtable}
}

\subsubsection{6.6 Latency Budget}\label{66-latency-budget}

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}ll@{}}
\toprule\noalign{}
Stage & Budget \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Raw event capture to durable log & under 250 ms median \\
Rolling-state update & under 1 s median \\
Candidate evaluation & under 50 ms \\
Episode ranker inference & under 10 ms CPU \\
Evidence fetch & 2-10 s async \\
Alert dispatch & under 1 s after final payload \\
\end{longtable}
}

\subsubsection{6.7 ML Feasibility and Local Compute
Constraints}\label{67-ml-feasibility-and-local-compute-constraints}

The v1 ML path is feasible on one local machine only if the system
reaches data-contract maturity first.

\paragraph{Feasible on local CPU}

\begin{itemize}
\tightlist
\item
  deterministic candidate generation,
\item
  rolling-window feature computation,
\item
  episode-level dataset materialization,
\item
  LightGBM or CatBoost training and calibration,
\item
  shadow-mode inference on candidate episodes,
\item
  replay, backtesting, and paper-trading evaluation.
\end{itemize}

\paragraph{Not yet feasible in the current repo state}

\begin{itemize}
\tightlist
\item
  Trustworthy model training is not ready while
  \texttt{ml\_pipeline/feature\_builder.py} remains a stub.
\item
  Gate 1 trade correctness must pass before wallet-aware features can be
  trusted.
\item
  Gate 2 replay must exist before labels, backtests, and feature windows
  are defendable.
\item
  Gate 5 episode training rows and labels must be stable before any
  learned ranker is graded as meaningful.
\end{itemize}

\paragraph{Canonical feasibility judgment}

The first ML system is feasible locally because the chosen model family
is tabular, CPU-cheap, and trained on engineered episode features rather
than raw high-frequency tensors. Deep models, graph neural networks, and
GPU-heavy sequence systems are not part of the defendable v1 path and
remain infeasible until the feature contract, replay path, and labeling
contract are stable.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{7. Evidence, Alerting, and Analyst
Workflow}\label{7-evidence-alerting-and-analyst-workflow}

\subsubsection{7.1 Evidence Workflow}\label{71-evidence-workflow}

External evidence is not a trigger. It is a confidence modifier and
explanation layer.

Canonical workflow:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Candidate is detected from market data alone.
\item
  Evidence worker queries X and web/news providers.
\item
  All queries and results are timestamped and cached.
\item
  Evidence state is classified as:

  \begin{itemize}
  \tightlist
  \item
    clear public explanation already exists,
  \item
    weak or partial public explanation,
  \item
    no reliable public explanation found.
  \end{itemize}
\item
  Alert is updated if evidence materially changes severity or
  interpretation.
\end{enumerate}

\subsubsection{7.2 Alert Severity
Definitions}\label{72-alert-severity-definitions}

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}ll@{}}
\toprule\noalign{}
Severity & Meaning \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
\texttt{INFO} & Interesting but not operationally useful \\
\texttt{WATCH} & Real anomaly worth monitoring \\
\texttt{ACTIONABLE} & Strong enough to demand immediate review \\
\texttt{CRITICAL} & Repeated or multi-source-confirmed high-value
event \\
\end{longtable}
}

\subsubsection{7.3 Alert Payload
Requirements}\label{73-alert-payload-requirements}

Every alert must include:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  what changed,
\item
  why it looks informed,
\item
  what market evidence supports it,
\item
  what public evidence exists or does not exist,
\item
  what invalidates it,
\item
  which model and feature version generated it.
\end{enumerate}

\subsubsection{7.4 Analyst Feedback
Requirements}\label{74-analyst-feedback-requirements}

Analyst feedback is mandatory. Each alert must support:

\begin{itemize}
\tightlist
\item
  acknowledge,
\item
  dismiss,
\item
  mark useful,
\item
  mark false positive,
\item
  attach notes,
\item
  attach follow-up timestamp.
\end{itemize}

Feedback becomes part of the labeled dataset.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{8. Replay, Backtesting, and
Validation}\label{8-replay-backtesting-and-validation}

\subsubsection{8.1 Replay Requirements}\label{81-replay-requirements}

The system is replayable only if it can:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  load raw archives for a historical window,
\item
  rebuild normalized envelopes,
\item
  rebuild local Redis-equivalent rolling state,
\item
  rerun candidate detection,
\item
  rerun ranking,
\item
  rehydrate evidence snapshots available at that time,
\item
  regenerate the final alert payload.
\end{enumerate}

\subsubsection{8.2 Required Validation
Designs}\label{82-required-validation-designs}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  time-split validation,
\item
  category holdout,
\item
  event-family holdout,
\item
  pre/post observability validation for H1,
\item
  ablation studies isolating wallet-aware value.
\end{enumerate}

\subsubsection{8.3 Paper-Trading Rules}\label{83-paper-trading-rules}

The canonical paper-trading simulator must:

\begin{itemize}
\tightlist
\item
  buy at ask and sell at bid by default,
\item
  apply platform fees,
\item
  model partial fills,
\item
  cap position size by available depth,
\item
  avoid unrealistic fills near resolution,
\item
  separate signal quality from execution assumptions.
\end{itemize}

\subsubsection{8.4 Success Metrics}\label{84-success-metrics}

Metrics are prioritized in this order:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  ranked alert precision and operational usefulness,
\item
  calibration,
\item
  lead time over public corroboration,
\item
  economic edge under conservative execution.
\end{enumerate}

Target thresholds are aspirational, not gating by themselves:

\begin{itemize}
\tightlist
\item
  Precision@10 \textgreater{} 0.60
\item
  Brier score \textless{} 0.20 for calibrated operational probabilities
\item
  median lead time \textgreater{} 30 minutes on the subset where
  corroboration exists
\item
  positive paper-trade edge after fees and slippage
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{9. Operations, Security, and
Governance}\label{9-operations-security-and-governance}

\subsubsection{9.1 Monitoring
Requirements}\label{91-monitoring-requirements}

The following metrics are mandatory:

\begin{itemize}
\tightlist
\item
  WS heartbeat lag
\item
  REST endpoint success/failure rate
\item
  archive write failures
\item
  local detector-input backlog
\item
  free disk headroom for archives and Postgres
\item
  Redis memory usage
\item
  PostgreSQL write latency
\item
  candidate rate by hour
\item
  alert rate by severity
\item
  evidence query latency and timeout rate
\end{itemize}

\subsubsection{9.2 Incident
Requirements}\label{92-incident-requirements}

\begin{itemize}
\tightlist
\item
  Pager notifications for collector death, archive failures, or
  zero-event periods.
\item
  Runbooks for reconnect storms, local disk pressure, and schema drift.
\item
  Daily integrity check comparing expected and actual event volume.
\end{itemize}

\subsubsection{9.3 Security
Requirements}\label{93-security-requirements}

\begin{itemize}
\tightlist
\item
  Secrets must live in the OS keychain, a local secret manager, or a
  file with restricted permissions, not in a casually shared
  \texttt{.env}.
\item
  Production DB access must be role-scoped.
\item
  User-facing alerts must hash or redact wallet identifiers by default.
\item
  Every model deployment must be logged with version, timestamp, and
  operator.
\end{itemize}

\subsubsection{9.4 Governance Rules}\label{94-governance-rules}

\begin{itemize}
\tightlist
\item
  No user-facing output may call a wallet or cluster an insider.
\item
  Model outputs must be explainable enough for manual review.
\item
  Evidence retrieval providers must be abstracted so vendor changes do
  not rewrite the product.
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{10. Cost Model and Budget}\label{10-cost-model-and-budget}

\subsubsection{10.1 Budget Principles}\label{101-budget-principles}

The old \texttt{\$40-\$75/month} estimate is rejected.

It ignored:

\begin{itemize}
\tightlist
\item
  local machine power and uptime assumptions,
\item
  local storage growth and backup needs,
\item
  dedicated PostgreSQL and Redis resource needs,
\item
  raw archive growth,
\item
  evidence-provider spend,
\item
  monitoring, log storage, and optional hardware upgrades.
\end{itemize}

\subsubsection{10.2 Canonical Budget
Assumptions}\label{102-canonical-budget-assumptions}

The v1 research environment assumes:

\begin{itemize}
\tightlist
\item
  one always-on local workstation or small server,
\item
  one persistent local collector process,
\item
  one local PostgreSQL instance,
\item
  one local Redis instance,
\item
  raw archive on local SSD or equivalent fast disk,
\item
  periodic backup of raw archives and the operational database,
\item
  local evidence and replay jobs,
\item
  no GPU,
\item
  no enterprise data contracts included.
\end{itemize}

\subsubsection{10.3 Monthly Budget
Model}\label{103-monthly-budget-model}

The following reflects a realistic local-first v1 research setup. It is
an incremental operating-cost model, not a claim that new hardware is
free. If a dedicated workstation must be purchased, that is a separate
capital decision.

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}llrl@{}}
\toprule\noalign{}
Item & Assumption & Estimated Monthly Cost & Notes \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Local compute and services & Existing workstation or small server &
\texttt{\$0-\$60} & Incremental power and wear; exclude sunk hardware if
already owned \\
Local PostgreSQL and Redis & Local services on the same machine &
\texttt{\$0-\$10} & Operational overhead, not a cloud bill \\
Hot archive storage & 200 GiB fast local storage &
\texttt{\$0-\$15} & Existing SSD if already available; otherwise
incremental storage cost \\
Cold backup storage & 1-2 TiB external disk or backup target &
\texttt{\$5-\$25} & Includes off-machine or removable backup discipline \\
Replay / evidence jobs & Local batch and async workers &
\texttt{\$0-\$10} & CPU time is covered by the local host assumption \\
Monitoring and logs & Local logs and lightweight monitoring &
\texttt{\$0-\$10} & Open-source or OS-native tooling \\
Telegram / Discord & Core alerting channels & \texttt{\$0} & API use
itself is free \\
Twilio SMS & Escalation only & \texttt{\$0-\$15} & Depends on alert
volume \\
X / web/news providers & Provider-specific & \texttt{\$50-\$500+} &
Highly vendor-dependent and must be budget-capped \\
\end{longtable}
}

\subsubsection{10.4 Budget Summary}\label{104-budget-summary}

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}lr@{}}
\toprule\noalign{}
Budget Tier & Monthly Range \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Core local infrastructure only & \texttt{\$5-\$120} \\
Core local infrastructure + basic evidence usage &
\texttt{\$55-\$620+} \\
Dedicated workstation plus heavier evidence usage &
\texttt{\$150-\$900+} monthly equivalent, plus optional one-time hardware
capex \\
\end{longtable}
}

\subsubsection{10.5 Budget Policy}\label{105-budget-policy}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Evidence providers must have explicit monthly spend caps.
\item
  If the local workstation cannot sustain PostgreSQL, Redis, archive
  writes, and detector latency simultaneously, optional scope must be
  frozen until capacity is increased.
\item
  Any move to dedicated extra hardware, cloud migration, or redundant
  collectors must trigger a budget review.
\end{enumerate}

\subsubsection{10.6 Budget Guardrails Derived from the
Audit}\label{106-budget-guardrails-derived-from-the-audit}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  No optional advanced-ML infrastructure spend is allowed before Gate 4
  is passed.
\item
  Evidence-provider usage must have both monthly caps and daily caps.
\item
  Archive growth, backup discipline, and evidence costs must be reviewed
  weekly during active development.
\item
  If real spend exceeds the documented plan by more than 20\% for two
  consecutive weeks, optional scope is frozen until a budget review is
  completed.
\item
  If an architectural choice is cheaper but makes replayability or data
  correctness worse, it is not acceptable for the canonical v1 path.
\end{enumerate}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{11. Roadmap and Stage
Gates}\label{11-roadmap-and-stage-gates}

\subsubsection{11.1 Stage Gates}\label{111-stage-gates}

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}lll@{}}
\toprule\noalign{}
Gate & Name & Must Be True Before Proceeding \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Gate 0 & Data Loss Stopped & No destructive TTL before archival, health
metrics live \\
Gate 1 & Ingestion Correct & Wallet-linked trades and both-side coverage
are working \\
Gate 2 & Replayable System & Raw archive, local detector input log, and
deterministic replay exist \\
Gate 3 & Online State Stable & Local Redis-backed features reconcile
against
replay \\
Gate 4 & Alert Loop Live & Alerts, suppression, and analyst feedback are
working \\
Gate 5 & Model Ready & Episode training rows and labels are
trustworthy \\
Gate 6 & Thesis Validation & Baselines, holdouts, and paper trading are
complete \\
\end{longtable}
}

\subsubsection{11.2 High-Level Phase
Map}\label{112-high-level-phase-map}

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}llll@{}}
\toprule\noalign{}
Phase & Focus & Deliverables & Duration \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
0 & Stop destructive behavior & Disable harmful TTL, add health metrics,
72h soak test & 1 week \\
1 & Ingestion correctness & Remove sports filter, both-side coverage,
wallet-linked trade schema & 1-2 weeks \\
2 & Durable data plane & Raw archive, local detector input log,
PostgreSQL cutover,
manifesting & 2-3 weeks \\
3 & Online state and candidates & Local Redis windows, deterministic
episodes,
cooldown logic & 2-3 weeks \\
4 & Evidence and alerts & Provider abstraction, Telegram/Discord,
analyst feedback loop & 2-3 weeks \\
5 & Replay and validation & Deterministic replay, backtests,
paper-trading simulator & 3-4 weeks \\
6 & ML v1 & LightGBM/CatBoost ranker, calibration, baseline comparisons
& 2-4 weeks \\
7 & Advanced research & Graph features, Hawkes/TCN experiments, H1 study
& after v1 stability \\
\end{longtable}
}

\subsubsection{11.3 Two-Person Team Operating
Model}\label{113-two-person-team-operating-model}

For a two-person team, the project must be split by system boundary, not
by random files.

\paragraph{Person A: Platform and Data Systems
Lead}\label{person-a-platform-and-data-systems-lead}

Primary ownership:

\begin{itemize}
\tightlist
\item
  collector runtime and ingestion correctness,
\item
  raw archive and detector-input infrastructure,
\item
  local PostgreSQL, local Redis, deployment, and monitoring,
\item
  replay plumbing, operational reliability, and cost control.
\end{itemize}

Primary success metric:

\begin{itemize}
\tightlist
\item
  the pipeline is durable, measurable, restart-safe, and replayable.
\end{itemize}

\paragraph{Person B: Detection, Research, and Product Intelligence
Lead}\label{person-b-detection-research-and-product-intelligence-lead}

Primary ownership:

\begin{itemize}
\tightlist
\item
  entity semantics and feature definitions,
\item
  candidate logic, alert logic, and evidence scoring,
\item
  replay validation, paper trading, and model evaluation,
\item
  model training, calibration, and analyst workflow design.
\end{itemize}

Primary success metric:

\begin{itemize}
\tightlist
\item
  the signals are explainable, testable, and empirically useful.
\end{itemize}

\paragraph{Shared Rules}\label{shared-rules}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Person A owns infrastructure contracts; Person B owns feature and
  labeling contracts.
\item
  No phase is done until both people sign off on the phase exit
  criteria.
\item
  Every phase must produce both code and validation artifacts.
\item
  Every interface between A and B must be written down in the SRS or
  adjacent design docs.
\item
  Person B does not build models on unstable data contracts.
\item
  Person A does not optimize infrastructure for features that are not
  yet defined.
\end{enumerate}

\paragraph{Weekly Cadence}\label{weekly-cadence}

\begin{itemize}
\tightlist
\item
  Monday: phase planning and dependency review.
\item
  Daily: 15-minute sync on blockers, schema changes, and handoffs.
\item
  Midweek: one integration checkpoint, not just parallel solo work.
\item
  End of week: gate review with evidence, screenshots, logs, and replay
  proof.
\end{itemize}

\subsubsection{11.4 Detailed Two-Person Phase
Plan}\label{114-detailed-two-person-phase-plan}

This is the canonical execution plan for a two-person team.

\paragraph{Phase 0: Stabilize the Existing
Collector}\label{phase-0-stabilize-the-existing-collector}

\textbf{Duration:} 1 week\\
\textbf{Goal:} Stop data loss and eliminate silent collector failure.

\textbf{Person A deliverables}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Add a configuration switch that disables destructive TTL deletion for
  closed-market data.
\item
  Add heartbeat metrics for:

  \begin{itemize}
  \tightlist
  \item
    last WebSocket event seen,
  \item
    last successful REST trade pull,
  \item
    last successful market sync,
  \item
    write failure count,
  \item
    reconnect count.
  \end{itemize}
\item
  Add structured logs for startup, reconnects, sync completion, and
  shutdown.
\item
  Add basic health-check scripts or commands that can verify the
  collector is alive.
\item
  Run and document a 72-hour soak test.
\end{enumerate}

\textbf{Person B deliverables}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Define the data-quality dashboard spec:

  \begin{itemize}
  \tightlist
  \item
    gap detection query,
  \item
    event-rate by source,
  \item
    stale-market detection,
  \item
    missing-trade-window checks.
  \end{itemize}
\item
  Create SQL validation queries for:

  \begin{itemize}
  \tightlist
  \item
    last event per source,
  \item
    zero-volume windows,
  \item
    snapshot cadence consistency,
  \item
    resolved-market retention.
  \end{itemize}
\item
  Produce a short baseline report on current collector failure modes.
\item
  Define the acceptance checklist for Gate 0 in a reusable markdown
  checklist.
\end{enumerate}

\textbf{Shared deliverables}

\begin{itemize}
\tightlist
\item
  one operational runbook for collector restart and health verification,
\item
  one 72-hour stability report,
\item
  one signed Gate 0 checklist.
\end{itemize}

\textbf{Phase exit criteria}

\begin{itemize}
\tightlist
\item
  no destructive TTL before archival,
\item
  metrics expose whether the collector is dead or stale,
\item
  both people can independently verify collector health.
\end{itemize}

\paragraph{Phase 1: Fix Ingestion
Correctness}\label{phase-1-fix-ingestion-correctness}

\textbf{Duration:} 1-2 weeks\\
\textbf{Goal:} Make the live data semantically usable for wallet-aware
detection.

\textbf{Person A deliverables}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Remove the hard-coded sports filter and replace it with a configurable
  universe selector.
\item
  Update live subscription logic so both YES and NO assets are covered.
\item
  Correct the trade ingestion path to capture the required
  condition-level identifiers.
\item
  Expand the schema and ingestion code for:

  \begin{itemize}
  \tightlist
  \item
    \texttt{proxy\_wallet},
  \item
    \texttt{transaction\_hash},
  \item
    \texttt{condition\_id},
  \item
    \texttt{asset\_id},
  \item
    \texttt{outcome\_side},
  \item
    \texttt{usdc\_notional}.
  \end{itemize}
\item
  Add dedupe keys and source-priority logic across WebSocket, REST, and
  backfill.
\end{enumerate}

\textbf{Person B deliverables}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Write the canonical entity and field validation spec for wallet-aware
  trades.
\item
  Build data-validation scripts for:

  \begin{itemize}
  \tightlist
  \item
    both-side asset coverage,
  \item
    duplicate trade inflation,
  \item
    null-rate of wallet fields,
  \item
    condition-id population rate.
  \end{itemize}
\item
  Define the first version of:

  \begin{itemize}
  \tightlist
  \item
    \texttt{first\_seen\_at},
  \item
    fresh-wallet flag logic,
  \item
    trade-to-market episode linkage rules.
  \end{itemize}
\item
  Produce a QA sample review over at least 20 manually inspected trade
  episodes.
\end{enumerate}

\textbf{Shared deliverables}

\begin{itemize}
\tightlist
\item
  one validated canonical trade schema,
\item
  one data-quality report proving both-side and wallet-linked coverage,
\item
  one Gate 1 signoff document.
\end{itemize}

\textbf{Phase exit criteria}

\begin{itemize}
\tightlist
\item
  wallet-linked trades are landing correctly,
\item
  YES/NO coverage is live,
\item
  duplicate inflation is understood and bounded.
\end{itemize}

\paragraph{Phase 2: Build the Durable Data
Plane}\label{phase-2-build-the-durable-data-plane}

\textbf{Duration:} 2-3 weeks\\
\textbf{Goal:} Make the system replayable and migrate canonical state
off SQLite.

\textbf{Person A deliverables}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Implement raw event envelope persistence for every inbound payload.
\item
  Write raw archives to local disk with deterministic partitioning and
  manifest tracking.
\item
  Stand up a local normalized-envelope log and publish detector inputs
  downstream.
\item
  Provision local PostgreSQL and migrate canonical write paths.
\item
  Add archive manifest tables, schema version tables, and operational
  migration notes.
\end{enumerate}

\textbf{Person B deliverables}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Define the normalized envelope contract consumed by the detector.
\item
  Build replay-validation tooling that:

  \begin{itemize}
  \tightlist
  \item
    replays a chosen archive window,
  \item
    compares replayed counts to original counts,
  \item
    verifies ordering and timestamp behavior.
  \end{itemize}
\item
  Define the point-in-time contract for profiles, activity, and evidence
  snapshots.
\item
  Produce one replay case study proving a one-hour window can be
  reconstructed.
\end{enumerate}

\textbf{Shared deliverables}

\begin{itemize}
\tightlist
\item
  one canonical raw-event schema,
\item
  one replay tool for historical partitions,
\item
  one local PostgreSQL-backed operational environment,
\item
  one Gate 2 replay proof.
\end{itemize}

\textbf{Phase exit criteria}

\begin{itemize}
\tightlist
\item
  raw archive exists and is immutable,
\item
  one-hour replay works end to end,
\item
  SQLite is no longer the authoritative operational source of truth.
\end{itemize}

\paragraph{Phase 3: Build Online State and Deterministic Candidate
Detection}\label{phase-3-build-online-state-and-deterministic-candidate-detection}

\textbf{Duration:} 2-3 weeks\\
\textbf{Goal:} Move from raw stream capture to stable episode
generation.

\textbf{Person A deliverables}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Stand up local Redis-backed rolling state for market, wallet, and
  event-family windows.
\item
  Implement watermark and late-event handling.
\item
  Build state reconciliation jobs that compare replayed state against
  live state.
\item
  Add throughput and memory monitoring for local Redis and detector
  workers.
\item
  Add persistent storage for candidate metadata and detector versions.
\end{enumerate}

\textbf{Person B deliverables}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Define the first complete episode feature set for:

  \begin{itemize}
  \tightlist
  \item
    fresh-wallet count,
  \item
    fresh-wallet notional share,
  \item
    directional imbalance,
  \item
    concentration ratio,
  \item
    probability velocity,
  \item
    probability acceleration,
  \item
    volume acceleration.
  \end{itemize}
\item
  Implement deterministic candidate rules and robust streaming
  statistics.
\item
  Define cooldown and suppression semantics for duplicate bursts.
\item
  Evaluate candidate quality on replayed historical windows and tune
  thresholds.
\end{enumerate}

\textbf{Shared deliverables}

\begin{itemize}
\tightlist
\item
  one live candidate-generation service,
\item
  one feature definition document with schema version,
\item
  one reconciliation report comparing live vs replayed features,
\item
  one Gate 3 signoff packet.
\end{itemize}

\textbf{Phase exit criteria}

\begin{itemize}
\tightlist
\item
  streaming features are stable,
\item
  candidate generation is reproducible,
\item
  the system emits candidates without flooding operators.
\end{itemize}

\paragraph{Phase 4: Build Evidence, Alerts, and Analyst
Workflow}\label{phase-4-build-evidence-alerts-and-analyst-workflow}

\textbf{Duration:} 2-3 weeks\\
\textbf{Goal:} Turn market anomalies into explainable human-facing
alerts.

\textbf{Person A deliverables}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Build provider abstractions for X and web/news retrieval.
\item
  Implement evidence workers with timeout handling, caching, and query
  logging.
\item
  Implement Telegram and Discord delivery integrations.
\item
  Persist alert delivery attempts, delivery status, and retry state.
\item
  Add secrets management and delivery monitoring.
\end{enumerate}

\textbf{Person B deliverables}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Define the evidence scoring rubric:

  \begin{itemize}
  \tightlist
  \item
    already public,
  \item
    weakly public,
  \item
    not publicly explained.
  \end{itemize}
\item
  Design the alert payload and explanation template.
\item
  Define severity thresholds and escalation rules.
\item
  Design analyst actions:

  \begin{itemize}
  \tightlist
  \item
    acknowledge,
  \item
    snooze,
  \item
    dismiss,
  \item
    mark useful,
  \item
    mark false positive,
  \item
    add notes.
  \end{itemize}
\item
  Run manual review on the first batch of live alerts and tune
  suppression rules.
\end{enumerate}

\textbf{Shared deliverables}

\begin{itemize}
\tightlist
\item
  one end-to-end alert path from candidate to Telegram,
\item
  one analyst-feedback table and workflow,
\item
  one alert suppression policy,
\item
  one Gate 4 signoff based on real alert traffic.
\end{itemize}

\textbf{Phase exit criteria}

\begin{itemize}
\tightlist
\item
  alerts are explainable and logged,
\item
  evidence snapshots are stored point in time,
\item
  analysts can respond to alerts in a structured way.
\end{itemize}

\paragraph{Phase 5: Build Replay, Backtesting, and
Validation}\label{phase-5-build-replay-backtesting-and-validation}

\textbf{Duration:} 3-4 weeks\\
\textbf{Goal:} Prove that the system can be trusted historically, not
just live.

\textbf{Person A deliverables}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Build batch replay jobs that reconstruct historical windows from raw
  archives.
\item
  Add backfill orchestration for missing windows and archive integrity
  checks.
\item
  Build result tables for replay runs, validation runs, and backtest
  artifacts.
\item
  Add reproducible job configuration and version tracking.
\end{enumerate}

\textbf{Person B deliverables}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Implement event-family holdout, category holdout, and time-split
  validation.
\item
  Build the conservative paper-trading simulator with:

  \begin{itemize}
  \tightlist
  \item
    bid/ask execution,
  \item
    slippage,
  \item
    size caps,
  \item
    fees,
  \item
    near-resolution restrictions.
  \end{itemize}
\item
  Define success metrics and failure metrics for:

  \begin{itemize}
  \tightlist
  \item
    candidate quality,
  \item
    alert usefulness,
  \item
    paper-trade edge,
  \item
    lead time.
  \end{itemize}
\item
  Produce at least three historical case studies that replay from raw
  data to alert decision.
\end{enumerate}

\textbf{Shared deliverables}

\begin{itemize}
\tightlist
\item
  one deterministic replay CLI or workflow,
\item
  one backtesting report template,
\item
  one historical validation pack,
\item
  one signed Gate 5 precondition report.
\end{itemize}

\textbf{Phase exit criteria}

\begin{itemize}
\tightlist
\item
  historical alerts are reproducible,
\item
  evaluation is point-in-time correct,
\item
  paper-trading assumptions are documented and conservative.
\end{itemize}

\paragraph{Phase 6: Train and Deploy ML
v1}\label{phase-6-train-and-deploy-ml-v1}

\textbf{Duration:} 2-4 weeks\\
\textbf{Goal:} Replace hand-ranked candidates with a learned ranker on
stable features.

\textbf{Person A deliverables}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Build feature materialization jobs for training and inference.
\item
  Add a model registry with:

  \begin{itemize}
  \tightlist
  \item
    artifact path,
  \item
    feature-schema version,
  \item
    training dataset hash,
  \item
    calibration metadata,
  \item
    deployment timestamp.
  \end{itemize}
\item
  Integrate the ranker into the detector or alert service in shadow mode
  first.
\item
  Log every score with model version and feature version.
\end{enumerate}

\textbf{Person B deliverables}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Build the episode training dataset.
\item
  Train the first LightGBM or CatBoost ranker.
\item
  Compare against the required baselines.
\item
  Calibrate outputs by market liquidity bucket and category.
\item
  Define the cutoffs for \texttt{WATCH}, \texttt{ACTIONABLE}, and
  \texttt{CRITICAL}.
\item
  Produce a model card describing failure modes and data limitations.
\end{enumerate}

\textbf{Shared deliverables}

\begin{itemize}
\tightlist
\item
  one shadow-deployed ranker,
\item
  one baseline-comparison report,
\item
  one calibration report,
\item
  one Gate 5 to Gate 6 transition memo.
\end{itemize}

\textbf{Phase exit criteria}

\begin{itemize}
\tightlist
\item
  the model outperforms wallet-unaware baselines,
\item
  score outputs are traceable and calibrated,
\item
  the model can be rolled back cleanly.
\end{itemize}

\paragraph{Phase 7: Advanced Research and
Scale-Up}\label{phase-7-advanced-research-and-scale-up}

\textbf{Duration:} after v1 stability\\
\textbf{Goal:} Expand from operational v1 into thesis-grade research
depth.

\textbf{Person A deliverables}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Improve system scale, reliability, and cost efficiency.
\item
  Add archival compaction, cold-storage policies, and long-run
  dashboards.
\item
  Add redundancy or HA only after the single-instance architecture is
  proven.
\end{enumerate}

\textbf{Person B deliverables}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Add graph-derived features and cluster persistence analysis.
\item
  Experiment with marked Hawkes or TCN sequence models.
\item
  Run the H1 observability / Goodhart study.
\item
  Produce ablation studies and thesis-quality result tables and figures.
\end{enumerate}

\textbf{Shared deliverables}

\begin{itemize}
\tightlist
\item
  one advanced research branch or experiment track,
\item
  one thesis / paper artifact set,
\item
  one post-v1 scaling plan.
\end{itemize}

\textbf{Phase exit criteria}

\begin{itemize}
\tightlist
\item
  advanced work is grounded in a stable operational core,
\item
  research outputs are reproducible from saved data and model versions.
\end{itemize}

\subsubsection{11.5 Stop Conditions}\label{115-stop-conditions}

The team must pause and revisit requirements if any of the following
happen:

\begin{itemize}
\tightlist
\item
  raw archive gaps exceed 1 hour,
\item
  duplicate trade inflation cannot be controlled,
\item
  alert false-positive rate remains operationally unusable after
  suppression tuning,
\item
  evidence-provider spend exceeds budget without measurable lift,
\item
  replay cannot reproduce a historical alert end to end.
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{12. External Sources}\label{12-external-sources}

\subsubsection{Platform and Market Data}\label{platform-and-market-data}

\begin{itemize}
\tightlist
\item
  Polymarket WebSocket overview:
  \url{https://docs.polymarket.com/quickstart/websocket/wss-overview}
\item
  Polymarket market channel:
  \url{https://docs.polymarket.com/quickstart/websocket/market-channel}
\item
  Polymarket trades API:
  \url{https://docs.polymarket.com/api-reference/core/get-trades-for-a-user-or-markets}
\item
  Polymarket activity API:
  \url{https://docs.polymarket.com/api-reference/core/get-user-activity}
\item
  Polymarket positions API:
  \url{https://docs.polymarket.com/api-reference/core/get-current-positions-for-a-user}
\item
  Polymarket public profile API:
  \url{https://docs.polymarket.com/api-reference/profiles/get-public-profile-by-wallet-address}
\item
  Polymarket traded-footprint API:
  \url{https://docs.polymarket.com/api-reference/misc/get-total-markets-a-user-has-traded}
\end{itemize}

\subsubsection{Historical Cloud Runtime and Cost
References}\label{gcp-runtime-and-cost-references}

These cloud references are retained only as optional future migration
material. They are not part of the canonical v1 deployment path.

\begin{itemize}
\tightlist
\item
  Cloud Run WebSockets:
  \url{https://cloud.google.com/run/docs/triggering/websockets}
\item
  Cloud Run request timeout:
  \url{https://cloud.google.com/run/docs/configuring/request-timeout}
\item
  Cloud Run pricing: \url{https://cloud.google.com/run/pricing}
\item
  Compute Engine VM pricing:
  \url{https://cloud.google.com/compute/all-pricing?hl=en}
\item
  Cloud SQL pricing: \url{https://cloud.google.com/sql/pricing}
\item
  Cloud SQL instance settings:
  \url{https://cloud.google.com/sql/docs/postgres/instance-settings}
\item
  Memorystore pricing:
  \url{https://cloud.google.com/memorystore/pricing}
\item
  Cloud Storage pricing:
  \url{https://cloud.google.com/storage/pricing?hl=en}
\item
  Pub/Sub pricing: \url{https://cloud.google.com/pubsub/pricing}
\end{itemize}

\subsubsection{Evidence Providers}\label{evidence-providers}

\begin{itemize}
\tightlist
\item
  X recent search overview:
  \url{https://docs.x.com/x-api/posts/search/recent-posts/introduction}
\item
  X rate limits: \url{https://docs.x.com/fundamentals/rate-limits}
\item
  Google Programmable Search JSON API overview:
  \url{https://developers.google.com/custom-search/v1/overview}
\end{itemize}

\subsubsection{Research References}\label{research-references}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Wolfers and Zitzewitz, "Prediction Markets" (NBER 2004)
\item
  Wolfers and Zitzewitz, "Prediction Markets in Theory and Practice"
  (NBER 2006)
\item
  Snowberg, Wolfers, and Zitzewitz, "How Prediction Markets Can Save
  Event Studies" (NBER 2011)
\item
  Snowberg, Wolfers, and Zitzewitz, "Prediction Markets for Economic
  Forecasting" (NBER 2012)
\item
  Oprea, Hanson, and Porter, "Affecting Policy by Manipulating
  Prediction Markets" (2012)
\item
  Yang and Zhu, "Back-Running: Seeking and Hiding Fundamental
  Information in Order Flows" (2015)
\item
  Easley, Lopez de Prado, and O\textquotesingle Hara, "The Volume Clock:
  Insights into the High Frequency Paradigm" (2012)
\end{enumerate}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\textbf{Final status:} This document replaces the old aspirational SRS
with an executable source of truth. The next engineering work should
follow Section 5 in order and should not skip Stage Gates.

\end{document}
